%%%%% ME

  @article{apolinario2019instantons,
    title={{Instantons and fluctuations in a Lagrangian model of turbulence}},
    author={Apolin{\'a}rio, G. B. and Moriconi, L. and Pereira, R. M.},
    journal={Physica A},
    volume={514},
    pages={741--757},
    year={2019},
    publisher={Elsevier}
  }

  @article{apolinario2019onset,
    title={{Onset of intermittency in stochastic Burgers hydrodynamics}},
    author={Apolin{\'a}rio, G. B. and Moriconi, L. and Pereira, R. M.},
    journal={Phys. Rev. E},
    volume={99},
    pages={033104},
    year={2019},
    publisher={APS}
  }
  
  @article{apolinario2020shotnoise,
	year = {2020},
	publisher = {{IOP} Publishing},
	volume = {2020},
	pages = {073208},
	author = {Apolin{\'{a}}rio, G. B. and Moriconi, L.},
	title = {Shot noise multifractal model for turbulent pseudo-dissipation},
	journal = {J. Stat. Mech.},
 }

  @book{schweber2012nuclear,
    title={{Nuclear forces: The making of the physicist Hans Bethe}},
    author={Schweber, S. S.},
    year={2012},
    publisher={Harvard University Press}
  }

  @article{eckert1999mathematics,
    title={{Mathematics, experiments, and theoretical physics: The early days of the Sommerfeld school}},
    author={Eckert, M.},
    journal={Physics in Perspective},
    volume={1},
    pages={238--252},
    year={1999},
    publisher={Springer}
  }

  @book{seth2010crafting,
    title={{Crafting the Quantum}},
    author={Seth, S.},
    year={2010},
    publisher={Cambridge: MIT Press}
  }

%%%%% Kolmogorov 1941

  @article{kolmogorov1941local,
    title={{The local structure of turbulence in incompressible viscous fluid for very large Reynolds numbers}},
    author={Kolmogorov, A. N.},
    journal={Cr Acad. Sci. URSS},
    volume={30},
    pages={301--305},
    year={1941}
  }

  @inproceedings{kolmogorov1941degeneration,
    title={{On degeneration (decay) of isotropic turbulence in an incompressible viscous liquid}},
    author={Kolmogorov, A. N.},
    booktitle={Dokl. Akad. Nauk SSSR},
    volume={31},
    pages={538--540},
    year={1941}
  }

  @inproceedings{kolmogorov1941dissipation,
    title={{Dissipation of energy in locally isotropic turbulence}},
    author={Kolmogorov, A. N.},
    booktitle={Akademiia Nauk SSSR Doklady},
    volume={32},
    pages={16},
    year={1941}
  }

  @article{richardson1922weather,
    title={{Weather prediction by numerical process cambridge university press}},
    author={Richardson, L. F.},
    journal={Cambridge Richardson Weather prediction by numerical process},
    volume={1922},
    year={1922}
  }

  @article{grant1962turbulence,
    title={{Turbulence spectra from a tidal channel}},
    author={Grant, H. L. and Stewart, R. W. and Moilliet, A.},
    journal={J. Fluid Mech.},
    volume={12},
    year={1962},
    publisher={Cambridge University Press}
  }
  % pages={241--268},

  @article{yeung2005,
    title={{High-Reynolds-number simulation of turbulent mixing}},
    author={Yeung, P. K. and Donzis, D. A. and Sreenivasan, K. R.},
    journal={Phys. Fluids},
    volume={17},
    pages={081703},
    year={2005},
    publisher={AIP}
  }


%%%%% Anomalous Dissipation = Zero Law

  @article{dryden1943review,
    title={{A review of the statistical theory of turbulence}},
    author={Dryden, H. L.},
    journal={Q. Appl. Math.},
    volume={1},
    pages={7--42},
    year={1943}
  }

  @article{cadot1997energy,
    title={{Energy injection in closed turbulent flows: Stirring through boundary layers versus inertial stirring}},
    author={Cadot, O. and Couder, Y. and Daerr, A. and Douady, S. and Tsinober, A.},
    journal={Phys. Rev. E},
    volume={56},
    pages={427},
    year={1997},
    publisher={APS}
  }

  @article{sreenivasan1984scaling,
    title={{On the scaling of the turbulence energy dissipation rate}},
    author={Sreenivasan, K. R.},
    journal={Phys. Fluids},
    volume={27},
    pages={1048--1051},
    year={1984},
    publisher={AIP}
  }

  @article{sreenivasan1998update,
    title={{An update on the energy dissipation rate in isotropic turbulence}},
    author={Sreenivasan, K. R.},
    journal={Phys. Fluids},
    volume={10},
    pages={528--529},
    year={1998},
    publisher={AIP}
  }

  @article{pearson2002measurements,
    title={{Measurements of the turbulent energy dissipation rate}},
    author={Pearson, B. R. and Krogstad, P.-{\AA}. and Van De Water, W.},
    journal={Phys. Fluids},
    volume={14},
    pages={1288--1290},
    year={2002},
    publisher={AIP}
  }

  @article{kaneda2003energy,
    title={{Energy dissipation rate and energy spectrum in high resolution direct numerical simulations of turbulence in a periodic box}},
    author={Kaneda, Y. and Ishihara, T. and Yokokawa, M. and Itakura, K. and Uno, A.},
    journal={Phys. Fluids},
    volume={15},
    pages={L21--L24},
    year={2003},
    publisher={AIP}
  }

  % H Nussenzveig, 2d instabilities
  @article{lacave2018asymptotic,
    title={{Asymptotic behavior of 2D incompressible ideal flow around small disks}},
    author={Lacave, C. and Lopes Filho, M. C. and Nussenzveig Lopes, H. J.},
    journal={Asymptotic Anal.},
    volume={108},
    pages={45--83},
    year={2018},
    publisher={IOS Press}
  }

  @article{nelkin1990multifractal,
    title={{Multifractal scaling of velocity derivatives in turbulence}},
    author={Nelkin, M.},
    journal={Phys. Rev. A},
    volume={42},
    pages={7226},
    year={1990},
    publisher={APS}
  }

  @phdthesis{drivas2017anomalous,
    title={{Anomalous Dissipation, Spontaneous Stochasticity \& Onsager's Conjecture}},
    author={Drivas, T. D.},
    year={2017},
    school={Johns Hopkins University}
  }

%%%%%% WEB

%https://tclf.org/sites/default/files/microsites/art-landscape/athena-tacha.html

%linux parallel, cite it

%%%%% WEB ARTICLES

  @misc{ball2014scientific,
    Author = {Ball, P.},
    Title  = "\emph{The Scientific Problem That Must Be Experienced}",
    Note   = "\url{http://nautil.us/issue/15/turbulence/the-scientific-problem-that-must-be-experienced} [Accessed: February 24th, 2020]",
    year = 2014,
  }

  @misc{ball2014feeling,
    Author = {Ball, P.},
    Title  = "\emph{ A Feeling for Flow }",
    Note   = "\url{http://philipball.blogspot.com/2014/07/a-feeling-for-flow.html}
             [Accessed: February 24th, 2020]",
    year = 2014,
  }

  @article{kemp2019leonardo,
   title={{Leonardo da Vinci’s laboratory: studies in flow}},
   volume={571},
   DOI={10.1038/d41586-019-02144-z},
   journal={Nature},
   publisher={Springer Science and Business Media LLC},
   author={Kemp, M.},
   year={2019},
   pages={322–323}
   }
   % url={http://dx.doi.org/10.1038/d41586-019-02144-z},
   % [Accessed: August 1st, 2019]

%%%%% REVIEWS

  @misc{eyink2008turbulence,
    Author = "G. L. Eyink",
    Title  = "Turbulence Theory: Course Notes",
    Note   = "\url{http://www.ams.jhu.edu/~eyink/Turbulence/notes.html}
             [Accessed: February 24th, 2020]",
    Year   = 2008,
  }

  @inbook{moriconi2008introducao,
    title={{Introdução \`{a} Teoria Estat\'{i}stica da Turbul\^{e}ncia}},
    author={L. Moriconi},
    booktitle={Turbul\^{e}ncia, volume 1 in Cole\c c\~{a}o cadernos de turbul\^{e}ncia},
    editor = {A. P. S. Freire and A. Ilha and M. J. Cola\c co},
    pages={37-97},
    publisher={ABCM, Rio de Janeiro},
    year={2008}
  }

  @book{monin2013statistical,
    title={{Statistical fluid mechanics, volume II: Mechanics of turbulence}},
    author={Monin, A. S. and Yaglom, A. M. and Lumley, J. L.},
    volume={2},
    year={2013},
    publisher={Courier Corporation}
  }
  %author={Monin, Andre{\u\i}} Sergeevich and Yaglom, Akiva M},

  @book{monin2007statistical,
    title={{Statistical Fluid Mechanics: Mechanics of Turbulence}},
    author={Monin, A. S. and Yaglom, A. M. and Lumley, J. L.},
    isbn={9780486458830},
    lccn={2006053473},
    series={Dover books on physics},
    year={2007},
    publisher={Dover Publications}
  }
  % url={https://books.google.com.br/books?id=EtTyyI4\_DvIC},

  @book{foias2001navier,
    title={{Navier-Stokes equations and turbulence}},
    author={Foias, C. and Manley, O. and Rosa, R. and Temam, R.},
    volume={83},
    year={2001},
    publisher={Cambridge University Press}
  }

  @book{kundu2008fluid,
    title={{Fluid Mechanics 4th}},
    author={Kundu, P. K. and Cohen, I. M. and Dowling, D. W.},
    year={2008},
    publisher={Elsevier}
  }

%%%%% MILLENIUM PRIZE

  @article{fefferman2006existence,
    title={{Existence and smoothness of the Navier-Stokes equation}},
    author={Fefferman, C. L.},
    journal={The Millennium Prize Problems},
    volume={57},
    pages={67},
    year={2006},
    publisher={Clay Math. Inst. Cambridge, MA}
  }

  @book{ladyzhenskaya1969mathematical,
    title={{The mathematical theory of viscous incompressible flow}},
    author={Ladyzhenskaya, O. A.},
    volume={2},
    year={1969},
    publisher={Gordon and Breach New York}
  }

%%%%% TURBULENCE AND DYNAMICAL SYSTEMS

  @article{lorenz1963,
    title={{Deterministic nonperiodic flow}},
    author={Lorenz, E. N.},
    journal={J. Atmos. Sci.},
    volume={20},
    pages={130--141},
    year={1963}
  }


  @inproceedings{landau1944problem,
    title={{On the problem of turbulence}},
    author={Landau, L. D.},
    booktitle={Dokl. Akad. Nauk USSR},
    volume={44},
    pages={311},
    year={1944}
  }

  @article{hopf1948mathematical,
    title={{A mathematical example displaying features of turbulence}},
    author={Hopf, E.},
    journal={Commun. Pur. Appl. Math.},
    volume={1},
    pages={303--322},
    year={1948},
    publisher={Wiley Online Library}
  }

%%%%% FUNCTIONAL

  @article{hopf1952statistical,
    title={{Statistical hydromechanics and functional calculus}},
    author={Hopf, E.},
    journal={J. Ration. Mech. Anal.},
    volume={1},
    pages={87--123},
    year={1952},
    publisher={JSTOR}
  }

  @article{kraichnan1958higher,
    title={{Higher order interactions in homogeneous turbulence theory}},
    author={Kraichnan, R. H.},
    journal={Phys. Fluids},
    volume={1},
    pages={358--359},
    year={1958},
    publisher={AIP}
  }

  @article{lewis1962space,
    title={{A space-time functional formalism for turbulence}},
    author={Lewis, R. M. and Kraichnan, R. H.},
    journal={Commun. Pur. Appl. Math.},
    volume={15},
    pages={397--411},
    year={1962},
    publisher={Wiley Online Library}
  }

  @article{tatarskii1962application,
    title={{Application of quantum field theory methods to the problem of degeneration of homogeneous turbulence}},
    author={Tatarskii, V. I.},
    journal={Sov. Phys. JETP},
    volume={15},
    year={1962}
  }

  @article{wyld1961formulation,
    title={{Formulation of the theory of turbulence in an incompressible fluid}},
    author={Wyld Jr, H. W.},
    journal={Ann. Phys.},
    volume={14},
    pages={143--165},
    year={1961},
    publisher={Elsevier}
  }

  @article{kraichnan1961dynamics,
    title={{Dynamics of nonlinear stochastic systems}},
    author={Kraichnan, R. H.},
    journal={J. Math. Phys.},
    volume={2},
    pages={124--148},
    year={1961},
    publisher={AIP}
  }

  @article{falkovich19932d,
  title={{Is 2D turbulence a conformal turbulence?}},
  author={Falkovich, G. and Hanany, A.},
  journal={Phys. Rev. Lett.},
  volume={71},
  pages={3454},
  year={1993},
  publisher={APS}
  }

  @article{falkovich1994universal,
  title={{Universal direct cascade in two-dimensional turbulence}},
  author={Falkovich, G. and Lebedev, V.},
  journal={Phys. Rev. E},
  volume={50},
  pages={3883},
  year={1994},
  publisher={APS}
  }

  @article{benzi1995conformal,
  title={{Conformal field theory and direct numerical simulation of two-dimensional turbulence}},
  author={Benzi, R. and Legras, B. and Parisi, G. and Scardovelli, R.},
  journal={Europhys. Lett.)},
  volume={29},
  pages={203},
  year={1995},
  publisher={IOP Publishing}
  }

  @article{polyakov1993theory,
  title={{The theory of turbulence in two dimensions}},
  author={Polyakov, A. M.},
  journal={Nucl. Phys. B},
  volume={396},
  pages={367--385},
  year={1993},
  publisher={Elsevier}
  }

  @article{onsager1953fluctuations,
  title={{Fluctuations and irreversible processes}},
  author={Onsager, L. and Machlup, S.},
  journal={Phys. Rev.},
  volume={91},
  pages={1505},
  year={1953},
  publisher={APS}
  }

  @article{phythian1977functional,
  title={{The functional formalism of classical statistical dynamics}},
  author={Phythian, R.},
  journal={J. Phys. A},
  volume={10},
  pages={777},
  year={1977},
  publisher={IOP Publishing}
  }

  @article{fournier1978infinite,
  title={{Infinite-dimensional turbulence}},
  author={Fournier, J. D. and Frisch, U. and Rose, H. A.},
  journal={J. Phys. A},
  volume={11},
  pages={187},
  year={1978},
  publisher={IOP Publishing}
  }

  @article{fournier1983remarks,
  title={{Remarks on the renormalization group in statistical fluid dynamics}},
  author={Fournier, J.-D. and Frisch, U.},
  journal={Phys. Rev. A},
  volume={28},
  pages={1000},
  year={1983},
  publisher={APS}
  }

  @article{canet2016fully,
    title={{Fully developed isotropic turbulence: Nonperturbative renormalization group formalism and fixed-point solution}},
    author={Canet, L. and Delamotte, B. and Wschebor, N.},
    journal={Phys. Rev. E},
    volume={93},
    pages={063101},
    year={2016},
    publisher={APS}
  }

  @article{tarpin2018stationary,
    title={{Stationary, isotropic and homogeneous two-dimensional turbulence: a first non-perturbative renormalisation group approach}},
    author={Tarpin, M. and Canet, L. and Pagani, C. and Wschebor, N.},
    journal={J. Phys. A},
    year={2018},
    publisher={IOP Publishing}
  }

  @article{canet2017spatiotemporal,
    title={{Spatiotemporal velocity-velocity correlation function in fully developed turbulence}},
    author={Canet, L. and Rossetto, V. and Wschebor, N. and Balarac, G.},
    journal={Phys. Rev. E},
    volume={95},
    pages={023107},
    year={2017},
    publisher={APS}
  }

  @article{langouche1979,
    title={{Functional integral methods for stochastic fields}},
    author={Langouche, F. and Roekaerts, D. and Tirapegui, E.},
    journal={Physica A},
    volume={95},
    pages={252--274},
    year={1979},
    publisher={Elsevier}
  }

  @article{jensen1981functional,
    title={{Functional integral approach to classical statistical dynamics}},
    author={Jensen, R. V.},
    journal={J. Stat. Phys.},
    volume={25},
    pages={183--210},
    year={1981},
    publisher={Springer}
  }

  @article{martin1973,
    title = {{Statistical Dynamics of Classical Systems}},
    author = {P. C. Martin and E. D. Siggia and H. A. Rose},
    journal = {Phys. Rev. A},
    volume = {\textbf{8}},
    issue = {1},
    pages = {423},
    year = 1973,
  }

  @article{dominicis1976,
    author = {C. de Dominicis},
    title = {{Techniques de Renormalization de la Theorie des Champs et Dynamique des Phenomenes Critques}},
    journal = {J. Phys. Colloques},
    year = 1976,
    volume = "\textbf{37}",
    pages = "247",
  }

  @article{janssen1976,
  title={{On a Lagrangean for classical field dynamics and renormalization group calculations of dynamical critical properties}},
  author={Janssen, H.-K.},
  journal={Z. Phys. B Con. Mat.},
  volume={23},
  pages={377--380},
  year={1976},
  publisher={Springer}
  }

%%%%% VIDEOS

  @misc{schaal2015kelvin,
    Author = "K. Schaal",
    Title  = "Kelvin-Helmholtz instability - Discontinuous Galerkin hydrodynamics",
    Note   = "\url{https://www.youtube.com/watch?v=cTRQP6DSaqA}
             [Accessed: February 24th, 2020]",
    Year   = 2015,
  }

  @misc{swiss2009technorama,
    Author = {T. R. Eisenberg},
    Title  = "Technorama Facade by Ned Khan",
    Note   = "\url{https://www.swiss-miss.com/2009/05/technorama-facade-by-ned-khan.html}
             [Accessed: February 24th, 2020]",
    Year   = 2009,
  }

%%%%% OTHERS

  @article{zeff2003,
   author={Zeff, B. W. and Lan\-ter\-man, D. D., and Mc\-A\-llis\-ter, R. and Roy, R. and Kos\-te\-lich, E. J. and La\-throp, D. P.},
   title={{Measuring intense rotation and dissipation in turbulent flows}},
   journal={Nature},
   pages=146,
   year=2003
  }

  @article{WallaceEF,
   author="V. Vukoslavcevic and N. Beratlis and E. Balaras and J. M. Wallace and O. Sun",
   title={{On the spatial resolution of velocity and velocity gradient-based turbulence statistics measured with multi-sensor hot-wire probes}},
   journal="Exp. Fluids",
   pages=109,
   year=2009
  }

  @article{wallace2009,
    author={J. Wallace},
    title={{Twenty years of experimental and direct numerical simulation access to the velocity gradient tensor: What have we learned about turbulence?}},
    journal={Phys. Fluids},
    pages={021301},
    year={2009}
  }

  @article{Martin98,
  author="J. Martin and C. Dopazo and L. Valino",
  title={{ Dynamics of velocity gradient invariants in turbulence: restricted Euler and linear diffusion models}},
  journal="Phys. Fluids",
  pages=2012,
  year=1998
  }

  @article{girimaji90diffusion,
  author={Girimaji, S. S. and Pope, S. B.},
  title={{A diffusion model for velocity gradients in turbulence}},
  journal="Phys. Fluids A",
  pages=242,
  year=1990
  }

  @article{Chertkov99,
  author="M. Chertkov and A. Pumir and B. I. Shraiman",
  title={{Lagrangian tetrad dynamics and the phenomenology of turbulence}},
  journal="Phys. Fluids",
  pages=2394,
  year=1999
  }

  @article{Jeong2003,
  author="E. Jeong and S. S. Girimaji",
  title={{Velocity-gradient dynamics in turbulence: effect of viscosity and forcing}},
  journal="Comput. Fluid Dyn.",
  pages=421,
  year=2003
  }

  @article{vukoslav91,
    title={{The velocity and vorticity vector fields of a turbulent boundary layer}},
    author={P. Vukoslavcevic and J. Wallace and J. L. Balint},
    journal={J. Fluid Mech.},
    volume={\textbf{228}},
    pages={25},
    year={1991},
  }

  @misc{LeoBouchet,
   author    = {Grigorio, L. S. and Bouchet, F. and Pereira, R. M. and Chevillard, L.},
   title     = {Instantons in a Lagrangian model of turbulence},
   archivePrefix = {arXiv},
   eprint        = {1608.07332},
   primaryClass  = {flu-dyn}
  }

  @book{TsinoberInformal,
    title={{An Informal Conceptual Introduction to Turbulence: Second Edition of An Informal Introduction to Turbulence}},
    author={A. Tsinober},
    year={2009},
    publisher={Springer Netherlands}
  }

  @article{MoriconiPereiraPRE,
    title = {Vorticity statistics and the time scales of turbulent strain},
    author = {L. Moriconi  and R. M. Pereira},
    journal = {Phys. Rev. E},
    volume = {\textbf{88}},
    issue = {1},
    pages = {013005},
    year = {2013}
    }

  @article{sreenivasan1997phenomenology,
    title={{The phenomenology of small-scale turbulence}},
    author={Sreenivasan, K. R. and Antonia, R. A.},
    journal={Annu. Rev. Fluid Mech.},
    volume={29},
    pages={435--472},
    year={1997},
    publisher={Annual Reviews 4139 El Camino Way, PO Box 10139, Palo Alto, CA 94303-0139, USA}
  }

  @article{dubrulle2019beyond,
    title={{Beyond Kolmogorov cascades}},
    author={Dubrulle, B.},
    journal={J. Fluid Mech.},
    volume={867},
    year={2019},
    publisher={Cambridge University Press}
  }

  @article{WallaceVukoslav2010,
    author="J. M. Wallace and P. V. Vukoslavcevic",
    title={{Experimental Measurement of the Velocity Gradient Tensor}},
    journal={Annu. Rev. of Fluid Mech.},
    pages={157},
    year={2010}
  }

  @article{KatzSheng2010,
    author={Katz, J. and Sheng, J.},
    title={{Applications of Holography in Fluid Mechanics and Particle Dynamics}},
    journal={Annu. Rev. Fluid Mech.},
    pages={531},
    year={2010}
  }

  @book{HolmesLumley,
    title={{Turbulence, Coherent Structures, Dynamical Systems and Symmetry}},
    author={P. Holmes and J. L. and Lumley and G. Berkooz},
    series={Cambridge Monographs on Mechanics},
    year={1998},
    publisher={Cambridge University Press}
  }

  @article{cardesa2017turbulent,
    title={{The turbulent cascade in five dimensions}},
    author={Cardesa, J. I. and Vela-Martin, A. and Jim{\'e}nez, J.},
    journal={Science},
    pages={eaan7933},
    year={2017},
    publisher={American Association for the Advancement of Science}
  }
  %author={Cardesa, J. I. and Vela-Mart{\'\i}n, A. and Jim{\'e}nez, J.},

  @article{bernard1998scaling,
    title={{Scaling and exotic regimes in decaying Burgers turbulence}},
    author={Bernard, D. and Gawedzki, K.},
    journal={J. Phys. A},
    volume={31},
    pages={8735},
    year={1998},
    publisher={IOP Publishing}
  }

  @article{falkovich2001particles,
    title={{Particles and fields in fluid turbulence}},
    author={Falkovich, G. and Gawedzki, K. and Vergassola, M.},
    journal={Rev. Mod. Phys.},
    volume={73},
    pages={913},
    year={2001},
    publisher={APS}
  }

  @article{gioia2010spectral,
    title={{Spectral theory of the turbulent mean-velocity profile}},
    author={Gioia, G. and Guttenberg, N. and Goldenfeld, N. and Chakraborty, P.},
    journal={Phys. Rev. Lett.},
    volume={105},
    pages={184501},
    year={2010},
    publisher={APS}
  }

  @article{yakhot2017emergence,
    title={{Emergence of multiscaling in a random-force stirred fluid}},
    author={Yakhot, V. and Donzis, D.},
    journal={Phys. Rev. Lett.},
    volume={119},
    pages={044501},
    year={2017},
    publisher={APS}
  }

  @article{yakhot1992renormalization,
    title={{The renormalization group, the $\varepsilon$-expansion and derivation of turbulence models}},
    author={Yakhot, V. and Smith, L. M.},
    journal={J. Sci. Comput.},
    volume={7},
    pages={35--61},
    year={1992},
    publisher={Springer}
  }

  @article{schumacher2007asymptotic,
    title={{Asymptotic exponents from low-Reynolds-number flows}},
    author={Schumacher, J. and Sreenivasan, K. R. and Yakhot, V.},
    journal={New J. Phys.},
    volume={9},
    pages={89},
    year={2007},
    publisher={IOP Publishing}
  }

  @article{yakhot2003pressure,
    title={{Pressure--velocity correlations and scaling exponents in turbulence}},
    author={Yakhot, V.},
    journal={J. Fluid Mech.},
    volume={495},
    pages={135--143},
    year={2003},
    publisher={Cambridge University Press}
  }

  @article{yakhot2014reynolds,
    title={{Reynolds number of transition and self-organized criticality of strong turbulence}},
    author={Yakhot, V.},
    journal={Phys. Rev. E},
    volume={90},
    pages={043019},
    year={2014},
    publisher={APS}
  }

  @article{friedrich2018,
    title={{Multiscale velocity correlations in turbulence and Burgers turbulence: Fusion rules, Markov processes in scale, and multifractal predictions}},
    author={Friedrich, J. and Margazoglou, G. and Biferale, L. and Grauer, R.},
    journal={Phys. Rev. E},
    volume={98},
    pages={023104},
    year={2018},
    publisher={APS}
  }

  @article{ishihara2009,
    title={{Study of high--Reynolds number isotropic turbulence by direct numerical simulation}},
    author={Ishihara, T. and Gotoh, T. and Kaneda, Y.},
    journal={Annu. Rev. Fluid Mech.},
    volume={41},
    year={2009},
    publisher={Annual Reviews}
  }

  @article{benzi2010inertial,
    title={{Inertial range Eulerian and Lagrangian statistics from numerical simulations of isotropic turbulence}},
    author={Benzi, R. and Biferale, L. and Fisher, R. and Lamb, D. Q. and Toschi, F.},
    journal={J. Fluid Mech.},
    volume={653},
    year={2010},
    publisher={Cambridge University Press}
  }


  @article{sinhuber2017dissipative,
    title={{Dissipative effects on inertial-range statistics at high Reynolds numbers}},
    author={Sinhuber, M. and Bewley, G. P. and Bodenschatz, E.},
    journal={Phys. Rev. Lett.},
    volume={119},
    year={2017},
    publisher={APS}
  }

  @article{iyer2017reynolds,
    title={{Reynolds number scaling of velocity increments in isotropic turbulence}},
    author={Iyer, K. P. and Sreenivasan, K. R. and Yeung, P. K.},
    journal={Phys. Rev. E},
    volume={95},
    year={2017},
    publisher={APS}
  }


  @article{reinke2018universal,
    title={{On universal features of the turbulent cascade in terms of non-equilibrium thermodynamics}},
    author={Reinke, N. and Fuchs, A. and Nickelsen, D. and Peinke, J.},
    journal={J. Fluid Mech.},
    volume={848},
    pages={117--153},
    year={2018},
    publisher={Cambridge University Press}
  }

  @article{mandelbrot1974intermittent,
    title={{Intermittent turbulence in self-similar cascades: divergence of high moments and dimension of the carrier}},
    author={Mandelbrot, B. B.},
    journal={J. Fluid Mech.},
    volume={62},
    pages={331--358},
    year={1974},
    publisher={Cambridge University Press}
  }

  @article{debue2018experimental,
    title={{Experimental test of the crossover between the inertial and the dissipative range in a turbulent swirling flow}},
    author={Debue, P. and Kuzzay, D. and Saw, E.-W. and Daviaud, F. and Dubrulle, B. and Canet, L. and Rossetto, V. and Wschebor, N.},
    journal={Phys. Rev. Fluids},
    volume={3},
    pages={024602},
    year={2018},
    publisher={APS}
  }

  %%%%% Large Deviation Theory

  @article{freidlin2004random,
    title={{Random perturbations of dynamical systems and diffusion processes with conservation laws}},
    author={Freidlin, M. and Weber, M.},
    journal={Probab. Theory Rel.},
    volume={128},
    pages={441--466},
    year={2004},
    publisher={Springer}
  }

  %%%%%

  @article{chevillard2007intermittency,
    title={{Intermittency and universality in a Lagrangian model of velocity gradients in three-dimensional turbulence}},
    author={Chevillard, L. and Meneveau, C.},
    journal={C. R. M{\'e}canique},
    volume={335},
    pages={187--193},
    year={2007},
    publisher={Elsevier}
  }

  % short journal names, refs stopped here

  @article{onsager1949statistical,
    title={{Statistical hydrodynamics}},
    author={Onsager, L.},
    journal={Nuovo Cimento},
    volume={6},
    pages={279--287},
    year={1949},
    publisher={Springer}
  }

  @article{taylor1938spectrum,
    title={{The spectrum of turbulence}},
    author={Taylor, G. I.},
    journal={Proc. R. Soc. Lon. Ser.-A},
    volume={164},
    pages={476--490},
    year={1938},
    publisher={The Royal Society}
  }

  @book{kahane1993some,
    title={{Some random series of functions}},
    author={Kahane, J.-P.},
    volume={5},
    year={1993},
    publisher={Cambridge University Press}
  }

  @article{ruelle1982large,
    title={{Large volume limit of the distribution of characteristic exponents in turbulence}},
    author={Ruelle, D.},
    journal={Commun. Math. Phys.},
    volume={87},
    pages={287--302},
    year={1982},
    publisher={Springer}
  }

  @article{vassilicos2015dissipation,
    title={{Dissipation in turbulent flows}},
    author={Vassilicos, J. C.},
    journal={Annu. Rev. Fluid Mech.},
    volume={47},
    pages={95--114},
    year={2015},
    publisher={Annual Reviews}
  }

  @article{bitane2013geometry,
    title={{Geometry and violent events in turbulent pair dispersion}},
    author={Bitane, R. and Homann, H. and Bec, J.},
    journal={J. Turbul.},
    volume={14},
    pages={23--45},
    year={2013},
    publisher={Taylor \& Francis}
  }

  @article{morozov1984langevin,
    title={{On the Langevin formalism for nonlinear and nonequilibrium hydrodynamic fluctuations}},
    author={Morozov, V. G.},
    journal={Physica A},
    volume={126},
    pages={443--460},
    year={1984},
    publisher={Elsevier}
  }

  @article{anselmet1984high,
    title={{High-order velocity structure functions in turbulent shear flows}},
    author={Anselmet, F. and Gagne, Y. and Hopfinger, E. J. and Antonia, R. A.},
    journal={J. Fluid Mech.},
    volume={140},
    pages={63--89},
    year={1984},
    publisher={Cambridge University Press}
  }

  @article{bernard1998slow,
    title={{Slow modes in passive advection}},
    author={Bernard, D. and Gawedzki, K. and Kupiainen, A.},
    journal={J. Stat. Phys.},
    volume={90},
    pages={519--569},
    year={1998},
    publisher={Springer}
  }

  @article{aurell1992multifractal,
    title={{On the multifractal properties of the energy dissipation derived from turbulence data}},
    author={Aurell, E. and Frisch, U. and Lutsko, J. and Vergassola, M.},
    journal={J. Fluid Mech.},
    volume={238},
    pages={467--486},
    year={1992},
    publisher={Cambridge University Press}
  }

  @article{dryden1941isotropic,
  title={{Isotropic turbulence in theory and experiment}},
  author={Dryden, H. L.},
  journal={T. von Karman Anniv},
  volume={85},
  year={1941}
  }

  @article{meneveau1987multifractal,
    title={{The multifractal spectrum of the dissipation field in turbulent flows}},
    author={Meneveau, C. and Sreenivasan, K. R.},
    journal={Nucl. Phys. B},
    volume={2},
    pages={49--76},
    year={1987},
    publisher={Elsevier}
  }

  @article{meneveau1991multifractal,
    title={{The multifractal nature of turbulent energy dissipation}},
    author={Meneveau, C. and Sreenivasan, K. R.},
    journal={J. Fluid Mech.},
    volume={224},
    pages={429--484},
    year={1991},
    publisher={Cambridge University Press}
  }

  @book{einstein1956investigations,
    title={{Investigations on the Theory of the Brownian Movement}},
    author={Einstein, A.},
    year={1956},
    publisher={Courier Corporation}
  }

  @article{langevin1908theorie,
    title={{Sur la th{\'e}orie du mouvement brownien}},
    author={Langevin, P.},
    journal={C. R. Acad. Sci. Paris.},
    volume={146},
    pages={530--533},
    year={1908}
  }

  @misc{cugliandolo2018building,
    title={Building a path-integral calculus},
    author={Cugliandolo, L. F. and Lecomte, V. and Van Wijland, F.},
    archivePrefix = {arXiv},
    eprint        = {1806.09486},
    primaryClass  = {cond-mat.stat-mech},
    year = {2018}
  }

  @article{nakazato1990symmetries,
    title={{Symmetries in stochastic quantization and Ito-Stratonovich related interpretation}},
    author={Nakazato, H. and Okano, K. and Schulke, L. and Yamanaka, Y.},
    journal={Nucl. Phys. B},
    volume={346},
    pages={611--631},
    year={1990},
    publisher={Elsevier}
  }
  % in fact, Sch{\"u}lke

  @article{galanti2004turbulence,
    title={{Is turbulence ergodic?}},
    author={Galanti, B. and Tsinober, A.},
    journal={Phys. Lett. A},
    volume={330},
    pages={173--180},
    year={2004},
    publisher={Elsevier}
  }

  @book{feynman2011feynmanvol2,
    title={{The Feynman Lectures on Physics}},
    author={Feynman, R. P. and Leighton, R. B. and Sands, M.},
    volume={II},
    year={2011},
    publisher={Basic books}
  }

  @article{taylor1938production,
    title={{Production and dissipation of vorticity in a turbulent fluid}},
    author={Taylor, G. I.},
    journal={Proc. R. Soc. Lon. Ser.-A},
    volume={164},
    pages={15--23},
    year={1938},
    publisher={The Royal Society London}
  }

  @article{ruelle1981differentiable,
    title={{Differentiable dynamical systems and the problem of turbulence}},
    author={Ruelle, D.},
    journal={B. Am. Math. Soc.},
    volume={5},
    pages={29--42},
    year={1981}
  }

  % Ergodic theory and birkhoff's theorem

  @book{cornfeld2012ergodic,
    title={{Ergodic theory}},
    author={Cornfeld, I. P. and Fomin, S. V. and Sinai, Y. G.},
    volume={245},
    year={2012},
    publisher={Springer Science \& Business Media}
  }

  @inproceedings{sinai1963,
    title={{On the foundations of the ergodic hypothesis for a dynamical system of statistical mechanics}},
    author={Sinai, Y. G.},
    booktitle={Doklady Akademii Nauk},
    volume={153},
    pages={1261--1264},
    year={1963},
    organization={Russian Academy of Sciences}
  }

  @book{dubois1999,
    title={{Dynamic multilevel methods and the numerical simulation of turbulence}},
    author={Dubois, T. and Jauberteau, F. and Temam, R.},
    year={1999},
    publisher={Cambridge University Press}
  }

  @book{fursikov1988,
    title={{Mathematical problems of statistical hydrodynamics}},
    author={Fursikov, A. W. and Vishik, M. I.},
    year={1988},
    publisher={Kluwer Academic Publisher, Dordrecht}
  }

  @article{ruelle1971,
    title={{On the nature of turbulence}},
    author={Ruelle, D. and Takens, F.},
    journal={Les rencontres physiciens-math{\'e}maticiens de Strasbourg-RCP25},
    volume={12},
    pages={1--44},
    year={1971}
  }



%%%%% LAGRANGIAN CHAPTER

  @article{borgas1993multifractal,
    title={{The multifractal Lagrangian nature of turbulence}},
    author={Borgas, M. S.},
    journal={Philos. T. R. Soc. Lond.},
    volume={342},
    pages={379--411},
    year={1993},
    publisher={The Royal Society London}
  }

  @article{ott2000experimental,
    title={{An experimental investigation of the relative diffusion of particle pairs in three-dimensional turbulent flow}},
    author={Ott, S. and Mann, J.},
    journal={J. Fluid Mech.},
    volume={422},
    pages={207--223},
    year={2000},
    publisher={Cambridge University Press}
  }

  @article{biferale2004multifractal,
    title={{Multifractal statistics of Lagrangian velocity and acceleration in turbulence}},
    author={Biferale, L. and Boffetta, G. and Celani, A. and Devenish, B. J. and Lanotte, A. and Toschi, F.},
    journal={Phys. Rev. Lett.},
    volume={93},
    pages={064502},
    year={2004},
    publisher={APS}
  }

  @article{hartman2002ordinary,
    title={{Ordinary Differential Equations, Classics in Applied Mathematics}},
    author={Hartman, P.},
    journal={Society for Industrial and Applied Mathematics (SIAM), Philadelphia, PA},
    volume={38},
    year={2002}
  }

  @article{richardson1926atmospheric,
    title={{Atmospheric diffusion shown on a distance-neighbour graph}},
    author={Richardson, L. F.},
    journal={Proc. R. Soc. Lon. Ser.-A},
    volume={110},
    pages={709--737},
    year={1926},
    publisher={The Royal Society London}
  }

  @article{das2019reynolds,
    title={{On the Reynolds number dependence of velocity-gradient structure and dynamics}},
    author={Das, R. and Girimaji, S. S.},
    journal={J. Fluid Mech.},
    volume={861},
    pages={163--179},
    year={2019},
    publisher={Cambridge University Press}
  }

  @article{watteaux2019time,
    title={{On the time scales and structure of Lagrangian intermittency in homogeneous isotropic turbulence}},
    author={Watteaux, R. and Sardina, G. and Brandt, L. and Iudicone, D.},
    journal={J. Fluid Mech.},
    volume={867},
    pages={438--481},
    year={2019},
    publisher={Cambridge University Press}
  }

  @article{meneveau2011lagrangian,
    title={{Lagrangian dynamics and models of the velocity gradient tensor in turbulent flows}},
    author={Meneveau, C.},
    journal={Annu. Rev. Fluid Mech.},
    volume={43},
    pages={219--245},
    year={2011},
    publisher={Annual Reviews}
  }

  @article{cantwell1992exact,
    title={{Exact solution of a restricted Euler equation for the velocity gradient tensor}},
    author={Cantwell, B. J.},
    journal={Phys. Fluids A},
    volume={4},
    pages={782--793},
    year={1992},
    publisher={AIP}
  }

  @article{ashurst1987alignment,
    title={{Alignment of vorticity and scalar gradient with strain rate in simulated Navier--Stokes turbulence}},
    author={Ashurst, W. T. and Kerstein, A. R. and Kerr, R. M. and Gibson, C. H.},
    journal={Phys. Fluids},
    volume={30},
    pages={2343--2353},
    year={1987},
    publisher={AIP}
  }

  @article{constantin2008stochastic,
    title={{A stochastic Lagrangian representation of the three-dimensional incompressible Navier-Stokes equations}},
    author={Constantin, P. and Iyer, G.},
    journal={Commun. Pur. Appl. Math.},
    volume={61},
    pages={330--345},
    year={2008},
    publisher={Wiley Online Library}
  }

  @book{arnold1992ordinary,
    title={{Ordinary Differential Equations}},
    author={Arnold, V. I.},
    isbn={9783540548133},
    lccn={91044188},
    series={Springer Textbook},
    year={1992},
    publisher={Springer Berlin Heidelberg}
  }

  @article{sawford2001turbulent,
    title={{Turbulent relative dispersion}},
    author={Sawford, B.},
    journal={Annu. Rev. Fluid Mech.},
    volume={33},
    pages={289--317},
    year={2001},
    publisher={Annual Reviews 4139 El Camino Way, PO Box 10139, Palo Alto, CA 94303-0139, USA}
  }

  @book{kunita1997stochastic,
    title={{Stochastic flows and stochastic differential equations}},
    author={Kunita, H.},
    volume={24},
    year={1997},
    publisher={Cambridge university press}
  }

  @article{taylor1922diffusion,
    title={{Diffusion by continuous movements}},
    author={Taylor, G. I.},
    journal={P. Lond. Math. Soc.},
    volume={2},
    pages={196--212},
    year={1922},
    publisher={Wiley Online Library}
  }

  @article{biferale2006lagrangian,
    title={{Lagrangian statistics in fully developed turbulence}},
    author={Biferale, L. and Boffetta, G. and Celani, A. and Lanotte, A. and Toschi, F.},
    journal={J. Turbul.},
    pages={N6},
    year={2006},
    publisher={Taylor \& Francis}
  }

  @article{mordant2001measurement,
    title={{Measurement of Lagrangian velocity in fully developed turbulence}},
    author={Mordant, N. and Metz, P. and Michel, O. and Pinton, J.-F.},
    journal={Phys. Rev. Lett.},
    volume={87},
    pages={214501},
    year={2001},
    publisher={APS}
  }

  @article{boffetta1999relative,
    title={{Relative dispersion in fully developed turbulence: Lagrangian statistics in synthetic flows}},
    author={Boffetta, G. and Celani, A. and Crisanti, A. and Vulpiani, A.},
    journal={Europhys. Lett.},
    volume={46},
    pages={177},
    year={1999},
    publisher={IOP Publishing}
  }

  @article{thomson2005particle,
    title={{Particle pair separation in kinematic simulations}},
    author={Thomson, D. J. and Devenish, B. J.},
    journal={J. Fluid Mech.},
    volume={526},
    pages={277--302},
    year={2005},
    publisher={Cambridge University Press}
  }

  @article{elliott1996pair,
    title={{Pair dispersion over an inertial range spanning many decades}},
    author={Elliott Jr., F. W. and Majda, A. J.},
    journal={Phys. Fluids},
    volume={8},
    pages={1052--1060},
    year={1996},
    publisher={AIP}
  }

%%%%% MULTIFRACTAL MODEL

  @inproceedings{frisch1985singularity,
    title={{On the singularity structure of fully developed turbulence}},
    author={Frisch, U. and Parisi, G.},
    booktitle={Turbulence and predictability in geophysical fluid dynamics and climate dynamics},
    editor={Ghil, M. and Benzi, R. and Parisi, G.},
    date={1985},
    booktitleaddon = {Proceedings of the International School of Physics E. Fermi},
    eventdate = {1983},
    venue = {Varenna, Italy},

  }

  @article{kestener2004generalizing,
    title={{Generalizing the wavelet-based multifractal formalism to random vector fields: application to three-dimensional turbulence velocity and vorticity data}},
    author={Kestener, P. and Arneodo, A.},
    journal={Phys. Rev. Lett.},
    volume={93},
    pages={044501},
    year={2004},
    publisher={APS}
  }

  @article{arneodo2008wavelet,
    title={{Wavelet-based multifractal analysis}},
    author={Arneodo, A. and Audit, B. and Kestener, P. and Roux, S.},
    journal={Scholarpedia},
    volume={3},
    pages={4103},
    year={2008}
  }

  @article{muzy1991wavelets,
    title={{Wavelets and multifractal formalism for singular signals: Application to turbulence data}},
    author={Muzy, J.-F. and Bacry, E. and Arneodo, A.},
    journal={Phys. Rev. Lett.},
    volume={67},
    pages={3515},
    year={1991},
    publisher={APS}
  }

  @article{parisi1985turbulence,
    title={{Turbulence and predictability in geophysical fluid dynamics}},
    author={Parisi, G.},
    journal={Proc. Intern. School of Physics' Enrico Fermi', 1983, Varenna, Italy},
    year={1985},
    publisher={North-Holland}
  }

%%%%% GALLERY

  @book{leal2003gallery,
    title={{A Gallery of Fluid Motion}},
    author={Leal, L. G. and Steen, P. H. and Samimy, M. and Breuer, K. S.},
    year={2003},
    publisher={Cambridge University Press}
  }

  @book{van1982album,
    title={{An album of fluid motion}},
    author={Van Dyke, M.},
    year={1982},
    publisher={Parabolic Press Stanford}
  }

  @misc{gfm,
      Author={{AMERICAN PHYSICAL SOCIETY}},
      Title  = "\emph{Gallery of Fluid Motion}",
      Note   = "\url{https://gfm.aps.org/} [Accessed: February 24th, 2020]",
      year = {2019},
  }

  @book{clarke2012water,
    title={{Water and art}},
    author={Clarke, D.},
    year={2012},
    publisher={Reaktion Books}
  }

  @book{leonardocodex,
    title={{Leonardo da Vinci's Codex Leicester: A New Edition (Volume 1)}},
    author={Laurenza, D. and Kemp, M.},
    year=2019,
    publisher={Oxford University Press}
  }

%%%%% NUMERICAL VALUES

  @misc{visc-water,
        Author = {{EN\-GI\-NEER\-ING TOOL\-BOX}},
        Title  = "\emph{Water - Dynamic and Kinematic Viscosity}",
        Note   = "\url{https://www.engineeringtoolbox.com/water-dynamic-kinematic-viscosity-d_596.html} [Accessed: February 24th, 2020]",
        year = {2004},
    }

  @misc{visc-air,
        Author = {{ENGINEERING TOOLBOX}},
        Title  = "\emph{Air - Dynamic and Kinematic Viscosity }",
        Note   = "\url{https://www.engineeringtoolbox.com/air-absolute-kinematic-viscosity-d_601.html}   [Accessed: February 24th, 2020]",
        year = {2003},
    }

%%%%% HISTORY

  @article{rott1990note,
    title={{Note on the history of the Reynolds number}},
    author={Rott, N.},
    journal={Annu. Rev. Fluid Mech.},
    volume={22},
    pages={1--12},
    year={1990},
    publisher={Annual Reviews 4139 El Camino Way, PO Box 10139, Palo Alto, CA 94303-0139, USA}
  }

%%%%% WAVELETS

  @article{farge1992wavelet,
    title={{Wavelet transforms and their applications to turbulence}},
    author={Farge, M.},
    journal={Annu. Rev. Fluid Mech.},
    volume={24},
    pages={395--458},
    year={1992},
    publisher={Annual reviews 4139 El Camino Way, PO Box 10139, Palo Alto, CA 94303-0139, USA}
  }

%%%%% SIMULATIONS

  @book{gottlieb1977numerical,
    title={{Numerical analysis of spectral methods: theory and applications}},
    author={Gottlieb, D. and Orszag, S. A.},
    volume={26},
    year={1977},
    publisher={Siam}
  }

%%%% SINGULARITIES

  @incollection{scheffer1976turbulence,
    title={{Turbulence and Hausdorff dimension}},
    author={Scheffer, V.},
    booktitle={Turbulence and Navier Stokes Equations},
    pages={174--183},
    year={1976},
    publisher={Springer}
  }

  @article{scheffer1980navier,
    title={{The Navier-Stokes equations on a bounded domain}},
    author={Scheffer, V.},
    journal={Commun. Math. Phys.},
    volume={73},
    pages={1--42},
    year={1980},
    publisher={Springer}
  }

%%%%% EXPERIMENTAL DATA

  @article{sreenivasan1995universality,
    title={{On the universality of the Kolmogorov constant}},
    author={Sreenivasan, K. R.},
    journal={Phys. Fluids},
    volume={7},
    year={1995},
    publisher={AIP}
  }

%%%%% BROWNIAN MOTION
% all of these should be reviewed for correctness, accents,

@book{thiele1880,
  title={{Sur la compensation de quelques erreurs quasi-syst{\'e}matiques par la m{\'e}thode des moindres carr{\'e}s}},
  author={Thiele, T. N.},
  year={1880},
  publisher={CA Reitzel, Copenhagen}
}

@incollection{jarrow2004,
  title={{A short history of stochastic integration and mathematical finance: the early years, 1880--1970}},
  author={Jarrow, R. and Protter, P.},
  booktitle={A festschrift for Herman Rubin},
  pages={75--91},
  year={2004},
  publisher={Institute of Mathematical Statistics}
}

@article{brown1828,
  title={{Mikroskopische Beobachtungen {\"u}ber die im Pollen der Pflanzen enthaltenen Partikeln, und {\"u}ber das allgemeine Vorkommen activer Molec{\"u}le in organischen und unorganischen K{\"o}rpern}},
  author={Brown, R.},
  journal={Ann. Phys.},
  volume={90},
  pages={294--313},
  year={1828},
  publisher={Wiley Online Library}
}

@article{einstein1905,
  title={{On the movement of small particles suspended in station-
ary liquid demanded by the molecular-kinetic theory of heat}},
  author={Einstein, A.},
  journal={Ann. Phys.-Leipzig},
  volume={31},
  pages={132},
  year={1905}
}

@article{sutherland1905lxxv,
  title={{LXXV. A dynamical theory of diffusion for non-electrolytes and the molecular mass of albumin}},
  author={Sutherland, W.},
  journal={The London, Edinburgh, and Dublin Philosophical Magazine and Journal of Science},
  volume={9},
  pages={781--785},
  year={1905},
  publisher={Taylor \& Francis}
}

@article{smoluchowski1906zusammenfassende,
  title={{ZUSAMMENFASSENDE BEARBEITUNGEN.}},
  author={Smoluchowski, Von M v and im unbegrenzten Raum, I Diffusion},
  journal={Ann. Phys.},
  volume={21},
  pages={756},
  year={1906}
}

@article{langevin1908cr,
  title={{CR Acad. Sci.(Paris) 146, 530; trans. Lemons, DS \& Gythiel, A.(1997)}},
  author={Langevin, P.},
  journal={Am. J. Phys},
  volume={65},
  pages={1079--1081},
  year={1908}
}

@article{perrin1908agitation,
  title={{L’agitation mol{\'e}culaire et le mouvement brownien}},
  author={Perrin, J.},
  journal={C. R. Hebd. Acad. Sci.},
  volume={146},
  pages={967--970},
  year={1908}
}

@article{perrin1909movement,
  title={{Movement brownien et realite molec}},
  author={Perrin, J.},
  journal={Ann. Chim. Phys.},
  volume={18},
  pages={1--114},
  year={1909}
}

%%%%% JHUTDB

@misc{jhtdb,
        Author = {{THE TURBULENCE DATABASE GROUP}},
        Title  = "\emph{Johns Hopkins Turbulence Databases}",
        Note   = "\url{http://turbulence.pha.jhu.edu}   [Accessed: February 24th, 2020]",
        year = {2019},
    }

%%%%% OBERLACK LIE SYMMETRIES

@article{grebenev2007approximate,
  title={{Approximate Lie symmetries of the Navier-Stokes equations}},
  author={Grebenev, V. N. and Oberlack, M.},
  journal={J. Nonlinear Math. Phys.},
  volume={14},
  pages={157--163},
  year={2007},
  publisher={Taylor \& Francis}
}

%%%%% THMT'18 CATALOG

  @book{thmt18,
    title={{Exposi{\c{c}}{\~a}o Turbul{\^e}ncia e Arte}},
    author={Guimar{\~a}es, H.},
    year={2018},
    publisher={UFRJ}
  }

%%%%% DISPERSION

@article{boffetta2002,
  title={{Relative dispersion in fully developed turbulence: the Richardson’s law and intermittency corrections}},
  author={Boffetta, G. and Sokolov, I. M.},
  journal={Phys. Rev. Lett.},
  volume={88},
  pages={094501},
  year={2002},
  publisher={APS}
}

@article{salazar2009,
  title={{Two-particle dispersion in isotropic turbulent flows}},
  author={Salazar, J. P. L. C. and Collins, L. R.},
  journal={Annu. Rev. Fluid Mech.},
  volume={41},
  pages={405--432},
  year={2009},
  publisher={Annual Reviews}
}

@article{bourgoin2006,
  title={{The role of pair dispersion in turbulent flow}},
  author={Bourgoin, M. and Ouellette, N. T. and Xu, H. and Berg, J. and Bodenschatz, E.},
  journal={Science},
  volume={311},
  pages={835--838},
  year={2006},
  publisher={American Association for the Advancement of Science}
}

%%%%% RG AND COARSE GRAINING

  @article{hou2001,
    title={{Renormalization group and perfect operators for stochastic differential equations}},
    author={Hou, Q. and Goldenfeld, N. and McKane, A.},
    journal={Phys. Rev. E},
    volume={63},
    pages={036125},
    year={2001},
    publisher={APS}
  }

  @article{goldenfeld1998,
    title={{Block spins for partial differential equations}},
    author={Goldenfeld, N. and McKane, A. and Hou, Q.},
    journal={J. Stat. Phys.},
    volume={93},
    pages={699--714},
    year={1998},
    publisher={Springer}
  }

  @article{chorin2002,
    title={{Optimal prediction with memory}},
    author={Chorin, A. J. and Hald, O. H. and Kupferman, R.},
    journal={Physica D},
    volume={166},
    pages={239--257},
    year={2002},
    publisher={Elsevier}
  }

  @article{chorin1999,
    title={{Unresolved computation and optimal predictions}},
    author={Chorin, A. J. and Kast, A. P. and Kupferman, R.},
    journal={Commun. Pur. Appl. Math.},
    volume={52},
    pages={1231--1254},
    year={1999},
    publisher={Wiley Online Library}
  }

  @article{chorin1998,
    title={{Optimal prediction of underresolved dynamics}},
    author={Chorin, A. J. and Kast, A. P. and Kupferman, R.},
    journal={P. Natl. Acad. Sci. USA},
    volume={95},
    pages={4094--4098},
    year={1998},
    publisher={National Acad Sciences}
  }

%%%%% RODRIGO THESIS

  @phdthesis{pereira2012,
    title={{Cascata log-poissoniana,flutua{\c{c}}{\~o}es de vorticidade e representa{\c{c}}{\~a}o de wavelets em turbul{\^e}ncia homog{\^e}nea}},
    author={Pereira, R. M.},
    year={2012},
    school={Universidade Federal do Rio de Janeiro}
  }

%%%%% INSTANTONS

  @article{schafer1998,
    title={{Instantons in QCD}},
    author={Sch{\"a}fer, T. and Shuryak, E. V.},
    journal={Rev. Mod. Phys.},
    volume={70},
    pages={323},
    year={1998},
    publisher={APS}
  }

@article{orszag1972,
  title={{Numerical simulation of three-dimensional homogeneous isotropic turbulence}},
  author={Orszag, S. A. and Patterson, G. S.},
  journal={Phys. Rev. Lett.},
  volume={28},
  pages={76},
  year={1972},
  publisher={APS}
}

@article{li2008,
  title={{A public turbulence database cluster and applications to study Lagrangian evolution of velocity increments in turbulence}},
  author={Li, Y. and Perlman, E. and Wan, M. and Yang, Y. and Meneveau, C. and Burns, R. and Chen, S. and Szalay, A. and Eyink, G.},
  journal={J. Turbul.},
  pages={N31},
  year={2008},
  publisher={Taylor \& Francis}
}


@book{schlichting2016,
  title={{Boundary-layer theory}},
  author={Schlichting, H. and Gersten, K.},
  year={2016},
  publisher={Springer}
}


@article{feynman1972,
  title={{Statistical Mechanics, A set of lectures}},
  author={Feynman, R. P.},
  journal={Frontiers in Physics. Perseus Books},
  year={1972}
}


  @article{eckert2017,
    title={{A kind of boundary-layer \enquote{flutter}: The turbulent history of a fluid mechanical instability}},
    author={Eckert, M.},
    journal={arXiv preprint arXiv:1706.00334},
    year={2017}
  }

  @article{lin1945,
    title={{On the stability of two-dimensional parallel flows. I. General theory}},
    author={Lin, C.-C.},
    journal={Q. Appl. Math.},
    volume={3},
    pages={117--142},
    year={1945}
  }

  @article{wiener1930generalized,
    title={{Generalized harmonic analysis}},
    author={Wiener, N.},
    journal={Acta Math.},
    volume={55},
    pages={117--258},
    year={1930},
    publisher={Institut Mittag-Leffler}
  }

  @article{taylor1935statistical,
    title={{Statistical theory of turbulence}},
    author={Taylor, G. I.},
    journal={Proc. R. Soc. Lon. Ser.-A},
    volume={151},
    pages={465--478},
    year={1935},
    publisher={The Royal Society}
  }

@article{benzi1993random,
  title={{A random process for the construction of multiaffine fields}},
  author={Benzi, R. and Biferale, L. and Crisanti, A. and Paladin, G. and Vergassola, M. and Vulpiani, A.},
  journal={Physica D},
  volume={65},
  pages={352--358},
  year={1993},
  publisher={Elsevier}
}

@inproceedings{kolmogorov1961precision,
    title={{Pr{\'e}cision sur la structure locale de la turbulence dans un fluide visqueux aux nombres de Reynolds {\'e}l{\'e}v{\'e}s}},
    author={Kolmogorov, A. N.},
    booktitle={M{\'e}canique de la Turbulence},
    year={1961},
    booktitleaddon = {Colloq. Internat. Marseille},
    published = {CNRS, Paris}
  }

@article{kolmogorov1962refinement,
  title={{A refinement of previous hypotheses concerning the local structure of turbulence in a viscous incompressible fluid at high Reynolds number}},
  author={Kolmogorov, A. N.},
  journal={J. Fluid Mech.},
  volume={13},
  pages={82--85},
  year={1962},
  publisher={Cambridge University Press}
}

@article{obukhov1962,
  title={{Some specific features of atmospheric turbulence}},
  author={Obukhov, A. M.},
  journal={J. Fluid Mech.},
  volume={13},
  pages={77--81},
  year={1962},
}

@article{reynolds1883,
  title={{XXIX. An experimental investigation of the circumstances which determine whether the motion of water shall be direct or sinuous, and of the law of resistance in parallel channels}},
  author={Reynolds, O.},
  journal={Philos. T. R. Soc. Lond.},
  pages={935--982},
  year={1883},
  publisher={The Royal Society London}
}

@article{duchon2000,
  title={{Inertial energy dissipation for weak solutions of incompressible Euler and Navier-Stokes equations}},
  author={Duchon, J. and Robert, R.},
  journal={Nonlinearity},
  volume={13},
  pages={249},
  year={2000},
  publisher={IOP Publishing}
}

@misc{tao2019onsager,
    Author = {Tao, T.},
    Title  = {{255B, Notes 2: Onsager’s conjecture}},
    Note   = "\url{https://terrytao.wordpress.com/2019/01/08/255b-notes-2-onsagers-conjecture/} [Accessed: February 24th, 2020]",
    year = 2019,
  }

@article{delellis2012,
  title={{Dissipative Euler flows and Onsager's conjecture}},
  author={De Lellis, C. and Sz{\'e}kelyhidi, L.},
  journal={arXiv preprint arXiv:1205.3626},
  year={2012}
}

@article{constantin1994,
  title={{Onsager's conjecture on the energy conservation for solutions of Euler's equation}},
  author={Constantin, P. and E, W. and Titi, E. S.},
  journal={Commun. Math. Phys.},
  volume={165},
  pages={207--209},
  year={1994},
  publisher={Springer}
}

@article{scheffer1993,
  title={{An inviscid flow with compact support in space-time}},
  author={Scheffer, V.},
  journal={J. Geom. Anal.},
  volume={3},
  pages={343--401},
  year={1993},
  publisher={Springer}
}

@article{shnirelman1997,
  title={{On the nonuniqueness of weak solution of the Euler equation}},
  author={Shnirelman, A.},
  journal={Commun. Pur. Appl. Math.},
  volume={50},
  pages={1261--1286},
  year={1997},
  publisher={Wiley Online Library}
}

@article{delellis2007,
  title={{The Euler equations as a differential inclusion}},
  author={De Lellis, C. and Sz{\'e}kelyhidi, L.},
  journal={arXiv preprint math/0702079},
  year={2007}
}

@article{isett2018,
  title={{A proof of Onsager's conjecture}},
  author={Isett, P.},
  journal={Ann. Math.},
  volume={188},
  pages={871--963},
  year={2018},
  publisher={JSTOR}
}

@article{delellis2019,
  title={{On turbulence and geometry: from Nash to Onsager}},
  author={De Lellis, C. and Sz{\'e}kelyhidi, L.},
  journal={arXiv preprint arXiv:1901.02318},
  year={2019}
}

@article{leray1934,
  title={{Sur le mouvement d'un liquide visqueux emplissant l'espace}},
  author={Leray, J.},
  journal={Acta Math.},
  volume={63},
  pages={193--248},
  year={1934},
  publisher={Institut Mittag-Leffler}
}

@article{hopf1950uber,
  title={{{\"U}ber die Anfangswertaufgabe f{\"u}r die hydrodynamischen Grundgleichungen. Erhard Schmidt zu seinem 75. Geburtstag gewidmet}},
  author={Hopf, E.},
  journal={Math. Nachr.},
  volume={4},
  pages={213--231},
  year={1950},
  publisher={Wiley Online Library}
}

@article{eyink2006,
  title={{Onsager and the theory of hydrodynamic turbulence}},
  author={Eyink, G. L. and Sreenivasan, K. R.},
  journal={Rev. Mod. Phys.},
  volume={78},
  pages={87},
  year={2006},
  publisher={APS}
}


@article{volino2001measurements,
  title={{Measurements in separated and transitional boundary layers under low-pressure turbine airfoil conditions}},
  author={Volino, R. J. and Hultgren, L. S.},
  journal={J. Turbomach.},
  volume={123},
  pages={189--197},
  year={2001},
  publisher={American Society of Mechanical Engineers Digital Collection}
}

@article{van1996modification,
  title={{{Modification of the boundary layer calculation in RFOIL for improved airfoil stall prediction}}},
  author={Van Rooij, R.},
  journal={Report IW-96087R TU-Delft, the Netherlands},
  year={1996}
}

  @book{mussardo2010,
    title={Statistical field theory: An introduction to exactly solved models in statistical physics},
    author={Mussardo, G.},
    year={2010},
    publisher={Oxford University Press}
  }

  @book{amit2005,
    title={{Field theory, the renormalization group, and critical phenomena: Graphs to computers}},
    author={Amit, D. J. and Martin-Mayor, V.},
    year={2005},
    publisher={World Scientific Publishing Company}
  }

  @book{francesco2012,
    title={Conformal field theory},
    author={Francesco, P. and Mathieu, P. and S{\'e}n{\'e}chal, D.},
    year={2012},
    publisher={Springer Science \& Business Media}
  }

%%%%% INSTANTONS HISTORY

@article{gurarie1996,
  title={{Instantons in the Burgers equation}},
  author={Gurarie, V. and Migdal, A.},
  journal={Phys. Rev. E},
  volume={54},
  pages={4908},
  year={1996},
  publisher={APS}
}


@article{balkovsky1997,
  title={{Intermittency of Burgers' turbulence}},
  author={Balkovsky, E. and Falkovich, G. and Kolokolov, I. and Lebedev, V.},
  journal={Phys. Rev. Lett.},
  volume={78},
  pages={1452},
  year={1997},
  publisher={APS}
}

@article{shraiman1994,
  title={{Lagrangian path integrals and fluctuations in random flow}},
  author={Shraiman, B. I. and Siggia, E. D.},
  journal={Phys. Rev. E},
  volume={49},
  pages={2912},
  year={1994},
  publisher={APS}
}

@article{falkovich1996,
  title={Instantons and intermittency},
  author={Falkovich, G. and Kolokolov, I. and Lebedev, V. and Migdal, A.},
  journal={Phys. Rev. E},
  volume={54},
  pages={4896},
  year={1996},
  publisher={APS}
}

@article{polyakov1995,
  title={Turbulence without pressure},
  author={Polyakov, A. M.},
  journal={Phys. Rev. E},
  volume={52},
  pages={6183},
  year={1995},
  publisher={APS}
}

@article{feigelman1980,
  title={One-dimensional periodic structure in a weak random potential},
  author={Feigel'Man, M. V.},
  journal={Soviet Journal of Experimental and Theoretical Physics},
  volume={52},
  pages={555},
  year={1980}
}

@article{cole1951,
  title={On a quasilinear parabolic equation occuring in aerodynamics},
  author={Cole, J. D.},
  journal={Quart. Appl. Math.},
  volume={9},
  pages={225-236},
  year={1951}
  }

@article{hopf1950,
  title={{The partial differential equation $u_t + u u_x = \mu u_{xx}$}},
  author={Hopf, E.},
  journal={Commun. Pur. Appl. Math.},
  volume={3},
  pages={201-230},
  year={1950}
  }

@article{bec2007,
  title={Burgers turbulence},
  author={Bec, J. and Khanin, K.},
  journal={Phys. Rep.},
  volume={447},
  pages={1-66},
  year={2007},
  publisher={Elsevier}
}

@article{chertkov1997,
  title={Instanton for random advection},
  author={Chertkov, M.},
  journal={Phys. Rev. E},
  volume={55},
  pages={2722},
  year={1997},
  publisher={APS}
}

@article{hayn1991,
  title={Instanton approach to the conductivity of a disordered solid},
  author={Hayn, R. and John, W.},
  journal={Nucl. Phys. B},
  volume={348},
  pages={766-786},
  year={1991},
  publisher={Elsevier}
}

@book{ellis2007,
  title={Entropy, large deviations, and statistical mechanics},
  author={Ellis, R. S.},
  year={2007},
  publisher={Springer}
}

@article{touchette2009,
  title={The large deviation approach to statistical mechanics},
  author={Touchette, H.},
  journal={Phys. Rep.},
  volume={478},
  pages={1-69},
  year={2009},
  publisher={Elsevier}
}

%%%%% BOOKS

@book{gardiner2009,
  title={Stochastic methods},
  author={Gardiner, C.},
  year={2009},
  published={Springer Berlin}
  }

@article{ito1944,
  title={Stochastic integral},
  author={It{\^o}, K.},
  journal={Proc. Imp. Acad. Jpn.},
  volume={20},
  pages={519--524},
  year={1944},
  publisher={The Japan Academy}
}

@inproceedings{bachelier1900,
  title={Th{\'e}orie de la sp{\'e}culation},
  author={Bachelier, L.},
  booktitle={Annales scientifiques de l'{\'E}cole normale sup{\'e}rieure},
  volume={17},
  pages={21--86},
  year={1900}
}

@book{vankampen1992,
  title={Stochastic processes in physics and chemistry},
  author={Van Kampen, N. G.},
  year={1992},
  publisher={Elsevier}
}

@article{mori1975,
  title={Stochastic processes of macroscopic variables},
  author={Mori, H.},
  journal={Prog. Theor. Phys.},
  volume={53},
  pages={1617},
  year={1975}
}

@book{protter2005,
  title={Stochastic differential equations},
  author={Protter, P.},
  year={2005},
  publisher={Springer}
}

@book{evans2012,
  title={An introduction to stochastic differential equations},
  author={Evans, L. C.},
  volume={82},
  year={2012},
  publisher={American Mathematical Soc.}
}

@article{vankampen1981,
  title={{It{\^o} versus Stratonovich}},
  author={Van Kampen, N. G.},
  journal={Journal of Statistical Physics},
  volume={24},
  pages={175--187},
  year={1981},
  publisher={Springer}
}

@article{mannella2012,
  title={It{\^o} versus Stratonovich: 30 years later},
  author={Mannella, R. and McClintock, P. V. E.},
  journal={Fluctuation and Noise Letters},
  volume={11},
  pages={1240010},
  year={2012},
  publisher={World Scientific}
}

%%%%% RFD references

@article{moriconi2014,
  title={{Velocity-gradient probability distribution functions in a Lagrangian model of turbulence}},
  author={Moriconi, L. and Pereira, R. M. and Grigorio, L. S.},
  journal={J. Stat. Mech.},
  volume={2014},
  pages={P10015},
  year={2014},
  publisher={IOP Publishing}
}

@article{johnson2016closure,
  title={A closure for Lagrangian velocity gradient evolution in turbulence using recent-deformation mapping of initially Gaussian fields},
  author={Johnson, P. L. and Meneveau, C.},
  journal={J. Fluid Mech.},
  volume={804},
  pages={387--419},
  year={2016},
  publisher={Cambridge University Press}
}

@book{Barabasi,
  title={Fractal concepts in surface growth},
  author={Barab{\'a}si, A.-L. and Stanley, H. E.},
  year={1995},
  publisher={Cambridge university press}
}

@article{chevillard2006,
  title = {Lagrangian dynamics and statistical geometric structure of turbulence},
  author = {Chevillard, L. and Meneveau, C.},
  journal = {Phys. Rev. Lett.},
  volume = {97},
  issue = {17},
  pages = {174501},
  year = {2006},
}

@article{pereira2018multifractal,
  title={A multifractal model for the velocity gradient dynamics in turbulent flows},
  author={Pereira, R. M. and Moriconi, L. and Chevillard, L.},
  journal={J. Fluid Mech.},
  volume={839},
  pages={430--467},
  year={2018},
  publisher={Cambridge University Press}
}

@article{chevillardetal2006,
author = {L. Chevillard and B. Castaing and E. Lévêque and A. Arneodo},
title = {Unified multifractal description of velocity increments statistics in turbulence: Intermittency and skewness },
journal = {Physica D},
volume = {218},
pages = {77},
year = {2006},
}


@article{kogut1979introduction,
  title={An introduction to lattice gauge theory and spin systems},
  author={Kogut, J. B.},
  journal={Rev. Mod. Phys.},
  volume={51},
  pages={659},
  year={1979},
  publisher={APS}
}

@book{feynman2010quantum,
  title={Quantum Mechanics and path integrals},
  author={Feynman, R. P. and Hibbs, A. R. and Styer, D. F.},
  year={2010},
  publisher={Courier Corporation}
}

@book{Peskin,
  title={An Introduction to Quantum Field Theory},
  author={Peskin, M. E. and Schroeder, D. V.},
  year=1995,
  publisher={Addison-Wesley Publishing Company}
}

@article{tsinober1992experimental,
  title={Experimental investigation of the field of velocity gradients in turbulent flows},
  author={Tsinober, A. and Kit, E. and Dracos, T.},
  journal={J. Fluid Mech.},
  volume={242},
  pages={169--192},
  year={1992},
  publisher={Cambridge University Press}
}

@article{she1994universal,
  title={Universal scaling laws in fully developed turbulence},
  author={She, Z.-S. and Leveque, E.},
  journal={Phys. Rev. Lett.},
  volume={72},
  pages={336},
  year={1994},
  publisher={APS}
}

@article{dubrulle1994intermittency,
  title={Intermittency in fully developed turbulence: Log-Poisson statistics and generalized scale covariance},
  author={Dubrulle, B.},
  journal={Phys. Rev. Lett.},
  volume={73},
  pages={959},
  year={1994},
  publisher={APS}
}

@article{girimaji90material,
  title={Material-element deformation in isotropic turbulence},
  author={Girimaji, S. S. and Pope, S. B.},
  journal={J. Fluid Mech.},
  volume={220},
  pages={427--458},
  year={1990},
  publisher={Cambridge University Press}
}

@article{chernykh2001,
  title={Large negative velocity gradients in Burgers turbulence},
  author={Chernykh, A. I. and Stepanov, M. G.},
  journal={Phys. Rev. E},
  volume={64},
  pages={026306},
  year={2001},
  publisher={APS}
}

@article{moriconi2004,
  title={Statistics of intense turbulent vorticity events},
  author={Moriconi, L.},
  journal={Phys. Rev. E},
  volume={70},
  pages={025302},
  year={2004},
  publisher={APS}
}

@article{falkovich2011,
  title={Vorticity statistics in the direct cascade of two-dimensional turbulence},
  author={Falkovich, G. and Lebedev, V.},
  journal={Phys. Rev. E},
  volume={83},
  pages={045301},
  year={2011},
  publisher={APS}
}

@article{grigorio2017instantons,
  title={Instantons in a Lagrangian model of turbulence},
  author={Grigorio, L. S. and Bouchet, F. and Pereira, R. M. and Chevillard, L.},
  journal={J. Phys. A},
  volume={50},
  pages={055501},
  year={2017},
  publisher={IOP Publishing}
}

@article{afonso2010recent,
  title={Recent fluid deformation closure for velocity gradient tensor dynamics in turbulence: Timescale effects and expansions},
  author={Afonso, M. M. and Meneveau, C.},
  journal={Physica D},
  volume={239},
  pages={1241--1250},
  year={2010},
  publisher={Elsevier}
}

@book{tsinober2009,
  title={An Informal Conceptual Introduction to Turbulence},
  author={A. Tsinober},
  year={2009},
  publisher={Springer Netherlands}
}

@article{moriconi2013,
  title = {Vorticity statistics and the time scales of turbulent strain},
  author = {Moriconi, L.  and Pereira, R. M.},
  journal = {Phys. Rev. E},
  volume = {88},
  issue = {1},
  pages = {013005},
  year = {2013}
  }

@article{kholmyansky2009,
  title = {Log-Poisson cascade description of turbulent velocity-gradient statistics},
  author = {Kholmyansky, M. and Moriconi, L. and Pereira, R. M. and Tsinober, A.},
  journal = {Phys. Rev. E},
  volume = {80},
  pages = {036311},
  year = {2009}
}

@article{batchelor1949,
  title={The nature of turbulent motion at large wave-numbers},
  author={Batchelor, G. K. and Townsend, A. A.},
  journal={P. Roy. Soc. Lond. A Mat.},
  volume={199},
  pages={238--255},
  year={1949}
}

@phdthesis{leorat1975,
  title={La turbulence magn{\'e}tohydrodynamique h{\'e}licitaire et la g{\'e}n{\'e}ration des champs magn{\'e}tiques a grande {\'e}chelle},
  author={Leorat, J.},
  school={Univ.Paris VII},
  year={1975}
}

@article{vieillefosse1982,
  title={Local interaction between vorticity and shear in a perfect incompressible fluid},
  author={Vieillefosse, P.},
  journal={J. Physique},
  volume={43},
  pages={837--842},
  year={1982},
  publisher={Soci{\'e}t{\'e} Fran{\c{c}}aise de Physique}
}

@article{vieillefosse1984,
  title={Internal motion of a small element of fluid in an inviscid flow},
  author={Vieillefosse, P.},
  journal={Physica A},
  volume={125},
  pages={150--162},
  year={1984},
  publisher={Elsevier}
}

@article{chevillard2008modeling,
  title={Modeling the pressure Hessian and viscous Laplacian in turbulence: comparisons with direct numerical simulation and implications on velocity gradient dynamics},
  author={Chevillard, L. and Meneveau, C. and Biferale, L. and Toschi, F.},
  journal={Phys. Fluids},
  volume={20},
  pages={101504},
  year={2008},
  publisher={AIP}
}

@book{pope2000,
  title={Turbulent flows},
  author={Pope, S. B.},
  year={2001},
  publisher={IOP Publishing}
}

%%%%% SADDLE POINT IN DISORDERED SYSTEMS

@article{zittartz1966,
  title={Theory of bound states in a random potential},
  author={Zittartz, J. and Langer, J. S.},
  journal={Phys. Rev.},
  volume={148},
  pages={741},
  year={1966},
  publisher={APS}
}

@article{langer1967,
  title={Theory of the condensation point},
  author={Langer, J. S.},
  journal={Ann. Physics},
  volume={41},
  pages={108-57},
  year={1967}
}

@article{langer1969,
  title={Statistical theory of the decay of metastable states},
  author={Langer, J. S.},
  journal={Ann. Phys.},
  volume={54},
  pages={258--275},
  year={1969}
}


@article{belavin1975,
  title={{Pseudoparticle solutions of the Yang-Mills equations}},
  author={Belavin, A. A. and Polyakov, A. M. and Schwartz, A. S. and Tyupkin, Y. S.},
  journal={Phys. Lett. B},
  volume={59},
  pages={85--87},
  year={1975}
}

@misc{canet2019leshouches,
  author        = {Canet, L.},
  title         = {Time dependence of correlation functions in homogeneous and isotropic turbulence},
  year          = {2019},
  institution = {Ecole de Physique des Houches},
  howpublished = {Lecture notes},
  note   = "\url{http://www.nctr.eu/images/2019/lectures/Lecture_Canet_NCTRV.pdf} [Accessed: February 24th, 2020]",
}

@misc{perrinAIP,
    Author = {{AMERICAN INSTITUTE OF PHYSICS}},
    Title  = {{Jean Perrin}},
    Note   = "\url{https://history.aip.org/phn/11807006.html} [Accessed: February 24th, 2020]",
    year = {2019},
  }

@article{forster1977,
  title={Large-distance and long-time properties of a randomly stirred fluid},
  author={Forster, D. and Nelson, D. R. and Stephen, M. J.},
  journal={Phys. Rev. A},
  volume={16},
  pages={732},
  year={1977},
  publisher={APS}
}


@article{varadhan1966,
  title={Asymptotic probabilities and differential equations},
  author={Varadhan, S. R. S.},
  journal={Commun. Pur. Appl. Math.},
  volume={19},
  pages={261--286},
  year={1966},
  publisher={Wiley Online Library}
}

@book{canuto2012spectral,
  title={Spectral methods in fluid dynamics},
  author={Canuto, C. and Hussaini, M. Y. and Quarteroni, A. and Thomas Jr, A.},
  year={2012},
  publisher={Springer Science \& Business Media}
}

@book{Kardar,
  title={Statistical physics of fields},
  author={Kardar, M.},
  year={2007},
  publisher={Cambridge University Press}
}

@article{ChevPRL,
  title = {Lagrangian dynamics and statistical geometric structure of turbulence},
  author = {Chevillard, L. and Meneveau, C.},
  journal = {Phys. Rev. Lett.},
  volume = {97},
  issue = {17},
  pages = {174501},
  numpages = {4},
  year = {2006},
}

@book{frisch1995,
  title={{Turbulence: The legacy of A. N. Kolmogorov}},
  author={U. Frisch},
  year={1995},
  publisher={Cambridge University Press}
}

@article{Chev2006,
author = {Chevillard, L. and Castaing, B. and Lévêque, E. and Arneodo, A.},
title = {Unified multifractal description of velocity increments statistics in turbulence: Intermittency and skewness },
journal = {Physica D},
volume = {218},
pages = {77},
year = {2006},
}

@book{zinn2002,
  title={Quantum Field Theory and Critical Phenomena},
  author={Zinn-Justin, J.},
  year=2002,
  publisher={Clarendon Press}
}



@article{Girimaji90,
  title={Material-element deformation in isotropic turbulence},
  author={Girimaji, SS and Pope, SB},
  journal={J. Fluid Mech.},
  volume={220},
  pages={427--458},
  year={1990},
  publisher={Cambridge University Press}
}

@article{Wallace9,
  title={The velocity and vorticity vector fields of a turbulent boundary layer},
  author={Vukoslavcevic, P. and Wallace, J. and Balint, J. L.},
  journal={J. Fluid Mech.},
  volume={228},
  pages={25},
  year={1991},
}

@article{grafke2015relevance,
  title={Relevance of instantons in Burgers turbulence},
  author={Grafke, T. and Grauer, R. and Sch{\"a}fer, T. and Vanden-Eijnden, E.},
  journal={Europhys. Lett.},
  volume={109},
  pages={34003},
  year={2015},
  publisher={IOP Publishing}
}

@article{grafke2015instanton,
  title={The instanton method and its numerical implementation in fluid mechanics},
  author={Grafke, T. and Grauer, R. and Sch{\"a}fer, T.},
  journal={J. Phys. A},
  volume={48},
  pages={333001},
  year={2015},
  publisher={IOP Publishing}
}

@article{MoriconiPereiraKholmyansky,
  title = {Log-Poisson cascade description of turbulent velocity-gradient statistics},
  author = {Kholmyansky, M. and Moriconi, L. and Pereira, R. M. and Tsinober, A.},
  journal = {Phys. Rev. E},
  volume = {80},
  pages = {036311},
  year = {2009}
}

@article{BatchelorTownsend1949,
  title={The nature of turbulent motion at large wave-numbers},
  author={Batchelor, G. K. and Townsend, A. A.},
  journal={P. Roy. Soc. Lond. A Mat.},
  volume={199},
  pages={238--255},
  year={1949}
}

@phdthesis{leorat1975turbulence,
  title={La turbulence magn{\'e}tohydrodynamique h{\'e}licitaire et la g{\'e}n{\'e}ration des champs magn{\'e}tiques a grande {\'e}chelle},
  author={Leorat, J.},
  school={Univ.Paris VII},
  year={1975}
}

@book{rajaraman1987,
  title={Solitons and Instantons: An Introduction to Solitons and Instantons in Quantum Field Theory},
  author={Rajaraman, R.},
  year={1987},
  publisher={Elsevier}
}

@article{burgers1948,
  author={Burgers, J. M.},
  title={A mathematical model illustrating the theory of turbulence},
  journal={Adv. Appl. Mech.},
  volume={1},
  page={171},
  year={1948}
}

@article{vonneumann1963,
  title={Recent theories of turbulence},
  author={von Neumann, J.},
  journal={Collected works (1949-1963)},
  volume={6},
  pages={437--472},
  year={1963},
  publisher={Pergamon Press}
}

@book{gurbatov1991,
  title={Nonlinear random waves and turbulence in nondispersive media: waves, rays, particles},
  author={Gurbatov, S. N. and Malakhov, A. N.},
  year={1991},
  publisher={Manchester University Press}
}

@article{zeldovich1970,
  title={{Gravitational instability: An approximate theory for large density perturbations}},
  author={Zel'Dovich, Ya. B.},
  journal={Astron. Astrophys.},
  volume={5},
  pages={84},
  year={1970}
}

@article{gurbatov1984,
  title={Probability distributions and spectra of potential hydrodynamic turbulence},
  author={Gurbatov, S. N. and Saichev, A. I.},
  journal={Radiofizika},
  volume={27},
  pages={456--468},
  year={1984}
}

@article{kardar1986,
  title={Dynamic scaling of growing interfaces},
  author={Kardar, M. and Parisi, G. and Zhang, Y.-C.},
  journal={Phys. Rev. Lett.},
  volume={56},
  pages={889},
  year={1986},
  publisher={APS}
}

@article{musha1978,
  title={{Traffic current fluctuation and the Burgers equation}},
  author={Musha, T. and Higuchi, H.},
  journal={Japanese journal of applied physics},
  volume={17},
  pages={811},
  year={1978},
  publisher={IOP Publishing}
}

@article{chowdhury2000,
  title={Statistical physics of vehicular traffic and some related systems},
  author={Chowdhury, D. and Santen, L. and Schadschneider, A.},
  journal={Phys. Rep.},
  volume={329},
  pages={199--329},
  year={2000},
  publisher={Elsevier}
}

@book{petrovskii2005,
  title={Exactly solvable models of biological invasion},
  author={Petrovskii, S. V. and Li, B.-L.},
  year={2005},
  publisher={Chapman and Hall/CRC}
}

@article{khanin1997,
  title={{Probability distribution functions for the random forced Burgers equation}},
  author={E, W. and Khanin, K. and Mazel, A. and Sinai, Y.},
  journal={Physical Review Letters},
  volume={78},
  pages={1904},
  year={1997},
  publisher={APS}
}

@article{bec2001,
  title={{Universality of velocity gradients in forced Burgers turbulence}},
  author={Bec, J.},
  journal={Phys. Rev. Lett.},
  volume={87},
  pages={104501},
  year={2001},
  publisher={APS}
}

@article{moriconi2009,
  title={{Instanton theory of Burgers shocks and intermittency}},
  author={Moriconi, L.},
  journal={Phys. Rev. E},
  volume={79},
  pages={046324},
  year={2009},
  publisher={APS}
}

@book{cardy1996,
  title={Scaling and renormalization in statistical physics},
  author={Cardy, J.},
  volume={5},
  year={1996},
  publisher={Cambridge university press}
}

@article{margazoglou2019,
  title={Hybrid monte carlo algorithm for sampling rare events in space-time histories of stochastic fields},
  author={Mar\-ga\-zo\-glou, G. and Bi\-fe\-ra\-le, L. and Gra\-uer, R. and Jan\-sen, K. and Mes\-ter\-h{\'a}\-zy, D. and Ro\-se\-now, T. and Tri\-pi\-cci\-one, R.},
  journal={Phys. Rev. E},
  volume={99},
  pages={053303},
  year={2019},
  publisher={APS}
}

@article{ebener2019,
  title={{Instanton based importance sampling for rare events in stochastic PDEs}},
  author={Ebener, L. and Margazoglou, G. and Friedrich, J. and Biferale, L. and Grauer, R.},
  journal={Chaos},
  volume={29},
  pages={063102},
  year={2019},
  publisher={AIP Publishing}
}

@article{gotoh1998,
  title={{Steady-state Burgers turbulence with large-scale forcing}},
  author={Gotoh, T. and Kraichnan, R. H.},
  journal={Phys. Fluids},
  volume={10},
  pages={2859--2866},
  year={1998},
  publisher={AIP}
}

@book{coleman1988,
  title={Aspects of symmetry},
  author={Coleman, S.},
  year={1988},
  publisher={Cambridge University Press}
}

@book{langouche1982,
  title={Functional integration and semiclassical expansions},
  author={Langouche, F. and Roekaerts, Dirk and Tirapegui, Enrique},
  year={1982},
  publisher={Springer Science \& Business Media}
}


@book{kloeden2013,
  title={Numerical solution of stochastic differential equations},
  author={Kloeden, P. E. and Platen, E.},
  volume={23},
  year={2013},
  publisher={Springer Science \& Business Media}
}

@article{smith1997,
  title={Onset of intermittency in two-dimensional decaying turbulence},
  author={Smith, L. M. and Yakhot, V.},
  journal={Phys. Rev. E},
  volume={55},
  pages={5458},
  year={1997},
  publisher={APS}
}

@article{forman1987,
  title={Functional determinants and geometry},
  author={Forman, R.},
  journal={Inventiones mathematicae},
  volume={88},
  pages={447--493},
  year={1987},
  publisher={Springer}
}

@article{mckane1995,
  author={McKane, A. J. and Tarlie, J. M. B.},
  journal={J. Phys. A},
  volume={28},
  page={6391},
  year={1995}
  }

@article{muratore2003,
  title={{Path integration over closed loops and Gutzwiller's trace formula}},
  author={Muratore-Ginanneschi, P.},
  journal={Phys. Rep.},
  volume={383},
  pages={299--397},
  year={2003},
  publisher={Elsevier}
}

@article{frisch2005,
  title={Does multifractal theory of turbulence have logarithms in the scaling relations?},
  author={Frisch, U. and Afonso, M. M. and Mazzino, A. and Yakhot, V.},
  journal={J. Fluid Mech.},
  volume={542},
  pages={97--103},
  year={2005},
  publisher={Cambridge University Press}
}

@misc{elgindi2019,
    title={{Finite-time singularity formation for $C^{1,α}$ solutions to the incompressible Euler equations on $\mathbb{R}^3$}},
    author={Elgindi, T. M.},
    year={2019},
    eprint={1904.04795},
    archivePrefix={arXiv},
    primaryClass={math.AP}
}

@misc{elgindighoul2019,
    title={{On the stability of self-similar blow-up for $C^{1,α}$ solutions to the incompressible Euler equations on $\mathbb{R}^3$}},
    author={Elgindi, T. M. and Ghoul, T.-E. and Masmoudi, N.},
    year={2019},
    eprint={1910.14071},
    archivePrefix={arXiv},
    primaryClass={math.AP}
}

@misc{hartnett2019euler,
   title={Famous Fluid Equations Spring a Leak},
   note="\url{https://www.quantamagazine.org/mathematician-makes-euler-equations-blow-up-20191218/}[Accessed: February 24th, 2020]",
   journal={Quanta magazine},
   author={Hartnett, K.},
   year={2019}
   }

% appendix cumulants
@article{cumulants,
  author = {McCullagh, P.  and Kolassa, J. },
  title   = {{C}umulants},
  year    = {2009},
  journal = {Scholarpedia},
  volume  = {4},
  pages   = {4699},
  DOI     = {10.4249/scholarpedia.4699},
  note    = {revision \#137322}
}

@misc{oeis_cumul,
    author = {{OEIS Foundation Inc.}},
    Title  = {A127671},
    Note   = "\url{http://oeis.org/A123456} [Accessed: February 24th, 2020]",
    year = {2019},
  }

@misc{novak2012,
    title={Three lectures on free probability},
    author={Novak, J. and LaCroix, M.},
    year={2012},
    eprint={1205.2097},
    archivePrefix={arXiv},
    primaryClass={math.CO}
}

@article{giardina2006,
  title={Direct evaluation of large-deviation functions},
  author={Giardina, C. and Kurchan, J. and Peliti, L.},
  journal={Phys. Rev. Lett.},
  volume={96},
  number={12},
  pages={120603},
  year={2006},
  publisher={APS}
}

@article{giardina2011,
  title={Simulating rare events in dynamical processes},
  author={Giardina, C. and Kurchan, J. and Lecomte, V. and Tailleur, J.},
  journal={J. Stat. Phys.},
  volume={145},
  pages={787--811},
  year={2011},
  publisher={Springer}
}

@article{perpete2011,
  title={A discrete log-normal process to sequentially generate a multifractal time series},
  author={Perp{\`e}te, N. and Schmitt, F. G.},
  journal={J. Stat. Mech.},
  volume={2011},
  pages={P12013},
  year={2011},
  publisher={IOP Publishing}
}

@article{iyer2019,
  title={{Circulation in high Reynolds number isotropic turbulence is a bifractal}},
  author={Iyer, K. P. and Sreenivasan, K. R. and Yeung, P. K.},
  journal={Phys. Rev. X},
  volume={9},
  pages={041006},
  year={2019},
  publisher={APS}
}

@book{ting2016,
  title={Basics of engineering turbulence},
  author={Ting, D.},
  year={2016},
  publisher={Academic Press}
}

@book{dewan2010,
  title={Tackling turbulent flows in engineering},
  author={Dewan, A.},
  year={2010},
  publisher={Springer Science \& Business Media}
}

@article{tao2016finite,
  title={{Finite time blowup for an averaged three-dimensional Navier-Stokes equation}},
  author={Tao, T.},
  journal={J. Am. Math. Soc.},
  volume={29},
  pages={601--674},
  year={2016}
}

@article{willert1991,
  title={Digital particle image velocimetry},
  author={Willert, C. E. and Gharib, M.},
  journal={Exp. Fluids},
  volume={10},
  pages={181--193},
  year={1991},
  publisher={Springer}
}


@article{adrian2005,
  title={Twenty years of particle image velocimetry},
  author={Adrian, R. J.},
  journal={Exp. Fluids},
  volume={39},
  pages={159--169},
  year={2005},
  publisher={Springer}
}

% limitations and hypotheses of the Navier-Stokes equations
@book{kremer2010,
  title={{An introduction to the Boltzmann equation and transport processes in gases}},
  author={Kremer, G. M.},
  year={2010},
  publisher={Springer Science \& Business Media}
}

@article{mejia2012,
  title={{Nonperturbative renormalization group study of the stochastic Navier-Stokes equation}},
  author={Mej{\'i}a-Mo\-nas\-te\-rio, C. and Mu\-ra\-to\-re-Gi\-nan\-nes\-chi, P.},
  journal={Phys. Rev. E},
  volume={86},
  pages={016315},
  year={2012},
  publisher={APS}
}

@article{furstenberg1963,
  title={The structure of distal flows},
  author={Furstenberg, H.},
  journal={Am. J. Math.},
  volume={85},
  pages={477--515},
  year={1963},
  publisher={JSTOR}
}

@article{zeldovich1984,
  title={Kinematic dynamo problem in a linear velocity field},
  author={Zel'Dovich, Ya. B. and Ruzmaikin, A. A. and Molchanov, S. A. and Sokoloff, D. D.},
  journal={J. Fluid Mech.},
  volume={144},
  pages={1--11},
  year={1984},
  publisher={Cambridge University Press}
}

@article{gawedzki2002,
  title={Soluble models of turbulent advection},
  author={Gawedzki, K.},
  journal={arXiv preprint nlin/0207058},
  year={2002}
}

@article{gawedzki2000,
  title={Phase transition in the passive scalar advection},
  author={Gawedzki, K. and Vergassola, M.},
  journal={Physica D},
  volume={138},
  pages={63--90},
  year={2000},
  publisher={Elsevier}
}

@misc{bernard2000,
  title={Turbulence for (and by) amateurs},
  author={Bernard, D.},
  archivePrefix = {arXiv},
  eprint        = {cond-mat/0007106},
  year = {2020}
}

@misc{perrinnobel,
  Author = {{NOBELPRIZE.ORG}},
  Title  = {Jean Baptiste Perrin - Nobel Lecture},
  Note   = "\url{https://www.nobelprize.org/prizes/physics/1926/perrin/lecture/} [Accessed: February 24th, 2020]",
  year = {2020},
}

@article{frisch1991global,
  title={{From global scaling, a la Kolmogorov, to local multifractal scaling in fully developed turbulence}},
  author={Frisch, U.},
  journal={P. Roy. Soc. Lond. A Mat.},
  volume={434},
  pages={89--99},
  year={1991},
  publisher={The Royal Society London}
}

@article{boffetta2017,
  title={Chaos and predictability of homogeneous-isotropic turbulence},
  author={Boffetta, G. and Musacchio, S.},
  journal={Phys. Rev. Lett.},
  volume={119},
  pages={054102},
  year={2017},
  publisher={APS}
}

@article{berera2018,
  title={Chaotic properties of a turbulent isotropic fluid},
  author={Berera, A. and Ho, R. D. J. G.},
  journal={Phys. Rev. Lett.},
  volume={120},
  pages={024101},
  year={2018},
  publisher={APS}
}

@article{eyink2011,
  title={Stochastic flux freezing and magnetic dynamo},
  author={Eyink, G. L.},
  journal={Phys. Rev. E},
  volume={83},
  pages={056405},
  year={2011},
  publisher={APS}
}

@article{bitane2013,
  title={Geometry and violent events in turbulent pair dispersion},
  author={Bitane, R. and Homann, H. and Bec, J.},
  journal={J. Turbul.},
  volume={14},
  pages={23--45},
  year={2013},
  publisher={Taylor \& Francis}
}

@article{dematteis2018,
  title={Rogue waves and large deviations in deep sea},
  author={Dematteis, G. and Grafke, T. and Vanden-Eijnden, E.},
  journal={P. Natl. Acad. Sci. USA},
  volume={115},
  pages={855--860},
  year={2018},
  publisher={National Acad Sciences}
}

@article{balkovsky1998instanton,
  title={{Instanton for the Kraichnan passive scalar problem}},
  author={Balkovsky, E. and Lebedev, V.},
  journal={Phys. Rev. E},
  volume={58},
  pages={5776},
  year={1998},
  publisher={APS}
}

@article{voth2017,
  title={Anisotropic particles in turbulence},
  author={Voth, G. and Soldati, A.},
  journal={Annu. Rev. Fluid Mech.},
  volume={49},
  pages={249--276},
  year={2017},
  publisher={Annual Reviews}
}

@article{rhodes2014,
  title={Gaussian multiplicative chaos and applications: a review},
  author={Rhodes, R. and Vargas, V.},
  journal={Probability Surveys},
  volume={11},
  year={2014}
}

@article{kahane1985,
  title={{Sur le chaos multiplicatif}},
  author={Kahane, J. P.},
  journal={Ann. Sci. Math. Québec},
  year={1985},
  volume={9},
  page={105}
}

@article{lejan2002,
  title={Integration of brownian vector fields},
  author={Le Jan, Y. and Raimond, O.},
  journal={Ann. Probab.},
  volume={30},
  pages={826--873},
  year={2002},
  publisher={Institute of Mathematical Statistics}
}

@misc{equationsproject,
  Author = {Bobroff, J.},
  Title  = {Physics reimagined},
  Note   = "\url{http://hebergement.u-psud.fr/supraconductivite/equationsnavier_en.html} [Accessed: February 24th, 2020]",
  year = {2012},
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%% new bib from shotnoise paper %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@incollection{mandelbrot1972,
  title={{Possible refinement of the lognormal hypothesis concerning the distribution of energy dissipation in intermittent turbulence}},
  author={Mandelbrot, B. B.},
  booktitle={Statistical models and turbulence},
  pages={333--351},
  year={1972},
  publisher={Springer}
}

@article{casella2011,
  title={{Exact simulation of jump-diffusion processes with Monte Carlo applications}},
  author={Casella, B. and Roberts, G. O.},
  journal={Methodol. Comput. Appl.},
  volume={13},
  pages={449--473},
  year={2011},
  publisher={Springer}
}

@book{klebaner2012,
  title={{Introduction to stochastic calculus with applications}},
  author={Klebaner, F. C.},
  year={2012},
  publisher={World Scientific Publishing Company}
}

@article{giesecke2013,
  title={{Exact sampling of jump diffusions}},
  author={Giesecke, K. and Smelov, D.},
  journal={Operations Research},
  volume={61},
  pages={894--907},
  year={2013},
  publisher={INFORMS}
}

@article{giesecke2011,
  title={{Exact simulation of point processes with stochastic intensities}},
  author={Giesecke, K. and Kakavand, H. and Mousavi, M.},
  journal={Oper. Res.},
  volume={59},
  pages={1233--1245},
  year={2011},
  publisher={INFORMS}
}

@article{pollock2016,
  title={On the exact and $\backslash\varepsilon$-strong simulation of (jump) diffusions},
  author={Pollock, M. and Johansen, A. M. and Roberts, G. O.},
  journal={Bernoulli},
  volume={22},
  pages={794--856},
  year={2016},
  publisher={Bernoulli Society for Mathematical Statistics and Probability}
}

@article{gonccalves2014,
  title={{Exact simulation problems for jump-diffusions}},
  author={Gon{\c{c}}alves, F. B. and Roberts, G. O.},
  journal={Methodol. Comput. Appl.},
  volume={16},
  pages={907--930},
  year={2014},
  publisher={Springer}
}

%%%%% Review on Lagrangian Statistics
@article{toschi2009,
  title={{Lagrangian properties of particles in turbulence}},
  author={Toschi, F. and Bodenschatz, E.},
  journal={Annu. Rev. Fluid Mech.},
  volume={41},
  pages={375--404},
  year={2009},
  publisher={Annual Reviews}
}

@article{berestycki2017,
  title={{An elementary approach to Gaussian multiplicative chaos}},
  author={Berestycki, N.},
  journal={Electron. Commun. Prob.},
  volume={22},
  year={2017},
  publisher={The Institute of Mathematical Statistics and the Bernoulli Society}
}

@article{schmitt2003,
  title={{A causal multifractal stochastic equation and its statistical properties}},
  author={Schmitt, F. G.},
  journal={Eur. Phys. J. B},
  volume={34},
  pages={85--98},
  year={2003},
  publisher={Springer}
}

@article{girimaji1990diffusion,
  title={{A diffusion model for velocity gradients in turbulence}},
  author={Girimaji, S. S. and Pope, S. B.},
  journal={Phys. Fluids A},
  volume={2},
  pages={242--256},
  year={1990},
  publisher={AIP}
}

@article{iyer2017,
  title={{Reynolds number scaling of velocity increments in isotropic turbulence}},
  author={Iyer, K. P. and Sreenivasan, K. R. and Yeung, P. K.},
  journal={Phys. Rev. E},
  volume={95},
  pages={021101},
  year={2017},
  publisher={APS}
}

@article{robert2010,
  title={{Gaussian multiplicative chaos revisited}},
  author={Robert, R. and Vargas, V.},
  journal={Ann. Probab.},
  volume={38},
  pages={605--631},
  year={2010},
  publisher={Institute of Mathematical Statistics}
}
% here they propose to make rigorous sense of the
% Mandelbrot limit-lognormal model

@article{drivas2019,
  title={{Turbulent cascade direction and Lagrangian time-asymmetry}},
  author={Drivas, T. D.},
  journal={J. Nonlinear Sci.},
  volume={29},
  year={2019},
  publisher={Springer}
}

@article{chevillard2017,
  title={{Regularized fractional Ornstein-Uhlenbeck processes and their relevance to the modeling of fluid turbulence}},
  author={Chevillard, L.},
  journal={Phys. Rev. E},
  volume={96},
  pages={033111},
  year={2017},
  publisher={APS}
}

@article{das2019,
  title={{On the Reynolds number dependence of velocity-gradient structure and dynamics}},
  author={Das, R. and Girimaji, S. S.},
  journal={J. Fluid Mech.},
  volume={861},
  pages={163--179},
  year={2019},
  publisher={Cambridge University Press}
}

@article{watteaux2019,
  title={{On the time scales and structure of Lagrangian intermittency in homogeneous isotropic turbulence}},
  author={Watteaux, R. and Sardina, G. and Brandt, L. and Iudicone, D.},
  journal={J. Fluid Mech.},
  volume={867},
  pages={438--481},
  year={2019},
  publisher={Cambridge University Press}
}

@article{schertzer1997,
  title={{Multifractal cascade dynamics and turbulent intermittency}},
  author={Schertzer, D. and Lovejoy, S. and Schmitt, F. G. and Chigirinskaya, Y. and Marsan, D.},
  journal={Fractals},
  volume={5},
  pages={427--471},
  year={1997},
  publisher={World Scientific}
}

@article{bacry2003,
  title={{Log-infinitely divisible multifractal processes}},
  author={Bacry, E. and Muzy, J.-F.},
  journal={Commun. Math. Phys.},
  volume={236},
  pages={449--475},
  year={2003},
  publisher={Springer}
}

@article{nguyen2019,
  title={Local estimates of H{\"o}lder exponents in turbulent vector fields},
  author={Nguyen, F. and Laval, J.-P. and Kestener, P. and Cheskidov, A. and Shvydkoy, R. and Dubrulle, B.},
  journal={Physical Review E},
  year={2019}
}

@article{johnson2016,
  title={{A closure for Lagrangian velocity gradient evolution in turbulence using recent-deformation mapping of initially Gaussian fields}},
  author={Johnson, P. L. and Meneveau, C.},
  journal={J. Fluid Mech.},
  volume={804},
  pages={387--419},
  year={2016},
  publisher={Cambridge University Press}
}

@article{wallace2010,
  title={{Measurement of the velocity gradient tensor in turbulent flows}},
  author={Wallace, J. M. and Vukoslav{\v{c}}evi{\'c}, P. V.},
  journal={Annu. Rev. Fluid Mech.},
  volume={42},
  pages={157--181},
  year={2010},
  publisher={Annual Reviews}
}

@article{meneveau2011,
  title={{Lagrangian dynamics and models of the velocity gradient tensor in turbulent flows}},
  author={Meneveau, C.},
  journal={Annu. Rev. Fluid Mech.},
  volume={43},
  pages={219--245},
  year={2011},
  publisher={Annual Reviews}
}

@article{vukoslav2009,
 author={Vukoslavcevic, V. and Beratlis, N. and Balaras, E. and Wallace, J. M. and Sun, O.},
 title={{On the spatial resolution of velocity and velocity gradient-based turbulence statistics measured with multi-sensor hot-wire probes}},
 journal={Exp. Fluids},
 pages={109},
 year={2009}
}

@article{das2002,
  title={The surprise element: jumps in interest rates},
  author={Das, S. R.},
  journal={J. Econometrics},
  volume={106},
  pages={27--65},
  year={2002},
  publisher={Elsevier}
}

@article{giraudo1997,
  title={{Jump-diffusion processes as models for neuronal activity}},
  author={Giraudo, M. T. and Sacerdote, L.},
  journal={Biosystems},
  volume={40},
  pages={75--82},
  year={1997},
  publisher={Elsevier}
}

@incollection{sacerdote2013,
  title={Stochastic integrate and fire models: a review on mathematical methods and their applications},
  author={Sacerdote, L. and Giraudo, M. T.},
  booktitle={Stoc. Biomath. Models},
  pages={99--148},
  year={2013},
  publisher={Springer}
}
% is this abbreviation correct?

@article{patel2008,
  title={{Stochastic resonance in continuous and spiking neuron models with Levy noise}},
  author={Patel, A. and Kosko, B.},
  journal={IEEE T. Neural Networks},
  volume={19},
  pages={1993--2008},
  year={2008},
  publisher={IEEE}
}

% Finances, First Jump Model
@article{cox1976,
  title={{The valuation of options for alternative stochastic processes}},
  author={Cox, J. C. and Ross, S. A.},
  journal={J. Financ. Econ.},
  volume={3},
  pages={145--166},
  year={1976},
  publisher={Elsevier}
}

% Finances, First Jump-Diffusion Model
@article{merton1976,
  title={{Option pricing when underlying stock returns are discontinuous}},
  author={Merton, R. C.},
  journal={J. Financ. Econ.},
  volume={3},
  pages={125--144},
  year={1976},
  publisher={Elsevier}
}

% Finances, Jump-Diffusion
@article{ball1993,
  title={{A jump diffusion model for the European Monetary System}},
  author={Ball, C. A. and Roma, A.},
  journal={J. Int. Money Financ.},
  volume={12},
  pages={475--492},
  year={1993},
  publisher={Elsevier}
}

@article{duffie2000,
  title={{Transform analysis and asset pricing for affine jump-diffusions}},
  author={Duffie, D. and Pan, J. and Singleton, K.},
  journal={Econometrica},
  volume={68},
  pages={1343--1376},
  year={2000},
  publisher={Wiley Online Library}
}

% Physics, Jump-Diffusion
@article{chudley1961,
  title={{Neutron scattering from a liquid on a jump diffusion model}},
  author={Chudley, C. T. and Elliott, R. J.},
  journal={P. Phys. Soc.},
  volume={77},
  pages={353},
  year={1961},
  publisher={IOP Publishing}
}

@article{funke1993,
  title={Jump relaxation in solid electrolytes},
  author={Funke, K.},
  journal={Prog. Solid State Ch.},
  volume={22},
  pages={111--195},
  year={1993},
  publisher={Elsevier}
}

@article{ellis1993,
  title={{Observation of jump diffusion of isolated sodium atoms on a Cu (001) surface by Helium atom scattering}},
  author={Ellis, J. and Toennies, J. P.},
  journal={Phys. Rev. Lett.},
  volume={70},
  pages={2118},
  year={1993},
  publisher={APS}
}

@article{montalenti1999,
  title={{Jumps and concerted moves in Cu, Ag, and Au (110) adatom self-diffusion}},
  author={Montalenti, F. and Ferrando, R.},
  journal={Phys. Rev. B},
  volume={59},
  pages={5881},
  year={1999},
  publisher={APS}
}

% Biomedicine, Jump-diffusion
@article{grenander1994,
  title={{Representations of knowledge in complex systems}},
  author={Grenander, U. and Miller, M. I.},
  journal={J. Roy. Stat. Soc. B Met.},
  volume={56},
  pages={549--581},
  year={1994},
  publisher={Wiley Online Library}
}

% Image recognition, jump-diffusion

@article{srivastava2002,
  title={{Jump--diffusion Markov processes on orthogonal groups for object pose estimation}},
  author={Srivastava, A. and Grenander, U. and Jensen, G. R. and Miller, M. I.},
  journal={J. Stat. Plan. Infer.},
  volume={103},
  pages={15--37},
  year={2002},
  publisher={Elsevier}
}

%%%%% Measure of Lagrangian Intermittency Parameter

@article{huang2014,
  title={{La\-gran\-gian cas\-ca\-de in three-dimensional ho\-mo\-ge\-neous and isotropic turbulence}},
  author={Huang, Y. and Schmitt, F. G.},
  journal={J. Fluid Mech.},
  volume={741},
  year={2014},
  publisher={Cambridge University Press}
}

%%%%% First Generation Cascade Models

@article{novikov1964,
  title={{The intermittency of turbulence and the spectrum of energy dissipation fluctuations}},
  author={Novikov, E. A. and Stewart, R. W.},
  journal={Izv. Geophys. Ser},
  volume={3},
  pages={408--413},
  year={1964}
}

@article{frisch1978,
  title={{A simple dynamical model of intermittent fully developed turbulence}},
  author={Frisch, U. and Sulem, P.-L. and Nelkin, M.},
  journal={J. Fluid Mech.},
  volume={87},
  pages={719--736},
  year={1978},
  publisher={Cambridge University Press}
}

@article{schertzer1984,
  title={{On the dimension of atmospheric motions}},
  author={Schertzer, D. and Lovejoy, S.},
  journal={Turbulence and Chaotic phenomena in Fluids},
  pages={505--512},
  year={1984},
  publisher={North-Holland}
}

@article{benzi1984,
  title={{On the multifractal nature of fully developed turbulence and chaotic systems}},
  author={Benzi, R. and Paladin, G. and Parisi, G. and Vulpiani, A.},
  journal={J. Phys. A},
  volume={17},
  pages={3521},
  year={1984},
  publisher={IOP Publishing}
}

@article{vainshtein1994,
  title={{Scaling exponents for turbulence and other random processes and their relationships with multifractal structure}},
  author={Vainshtein, S. I. and Sreenivasan, K. R. and Pierrehumbert, R. T. and Kashyap, V. and Juneja, A.},
  journal={Phys. Rev. E},
  volume={50},
  pages={1823},
  year={1994},
  publisher={APS}
}

@article{muzy2002,
  title={{Multifractal stationary random measures and multifractal random walks with log infinitely divisible scaling laws}},
  author={Muzy, J.-F. and Bacry, E.},
  journal={Phys. Rev. E},
  volume={66},
  pages={056121},
  year={2002},
  publisher={APS}
}

@article{muzy1994,
  title={{The multifractal formalism revisited with wavelets}},
  author={Muzy, J.-F. and Bacry, E. and Arneodo, A.},
  journal={Int. J. Bifurcat. Chaos},
  volume={4},
  pages={245--302},
  year={1994},
  publisher={World Scientific}
}

@article{ashurst1987,
  title={{Alignment of vorticity and scalar gradient with strain rate in simulated Navier--Stokes turbulence}},
  author={Ashurst, W. T. and Kerstein, A. R. and Kerr, R. M. and Gibson, C. H.},
  journal={Phys. Fluids},
  volume={30},
  pages={2343--2353},
  year={1987},
  publisher={AIP}
}

@article{kailasnath1992,
  title={{Probability density of velocity increments in turbulent flows}},
  author={Kailasnath, P. and Sreenivasan, K. R. and Stolovitzky, G.},
  journal={Phys. Rev. Lett.},
  volume={68},
  pages={2766},
  year={1992},
  publisher={APS}
}


@article{schumacher2014,
  title={{Small-scale universality in fluid turbulence}},
  author={Schumacher, J. and Scheel, J. D. and Krasnov, D. and Donzis, D. A. and Yakhot, V. and Sreenivasan, K. R.},
  journal={P. Natl. Acad. Sci. USA},
  volume={111},
  pages={10961--10965},
  year={2014},
  publisher={National Acad Sciences}
}

@article{benzi1991,
  title={{Multifractality in the statistics of the velocity gradients in turbulence}},
  author={Benzi, R. and Biferale, L. and Paladin, G. and Vulpiani, A. and Vergassola, M.},
  journal={Phys. Rev. Lett.},
  volume={67},
  pages={2299},
  year={1991},
  publisher={APS}
}

@article{biferale1993,
  title={{Probability distribution functions in turbulent flows and shell models}},
  author={Biferale, L.},
  journal={Phys. Fluids A},
  volume={5},
  pages={428--435},
  year={1993},
  publisher={AIP}
}

@article{castaing1990,
  title={{Velocity probability density functions of high Reynolds number turbulence}},
  author={Castaing, B. and Gagne, Y. and Hopfinger, E. J.},
  journal={Physica D},
  volume={46},
  pages={177--200},
  year={1990},
  publisher={Elsevier}
}

@article{gurvitch1963,
  title={On the experimental evaluation of the fluctuations of dissipation of turbulent energy},
  author={Gurvitch, A. S. and Zubkovski, S. L.},
  year={1963},
  journal={Izv. An. SSSR Geol.+},
  volume={12},
  pages={1856-1858}
  }
% Izv. Akad. Nauk. SSSR Ser. Geofiz.
% Izvestia, Geophysics Series (following the reference in Some Physical and Statistical Aspects of Clear Air Turbulence, Peter F. Lester)

@article{pond1965,
  title={Measurements of the statistical characteristics of small-scale turbulent motions},
  author={Pond, S. and Stewart, R. W.},
  year={1965},
  journal={Izv. An. SSSR Fiz. Atm.+},
  volume={1},
  page={914}
  }
% Styuart, he is Russian
% https://books.google.com.br/books?id=3U8qAAAAMAAJ&lpg=RA3-PA134&ots=r0g6BcZ-CV&dq=pond%20stewart%20izvestiya&pg=RA3-PA134#v=onepage&q=pond%20stewart%20izvestiya&f=false

@article{mandelbrot1974,
  title={Intermittent turbulence in self-similar cascades: divergence of high moments and dimension of the carrier},
  author={Mandelbrot, B. B.},
  journal={J. Fluid Mech.},
  volume={62},
  pages={331--358},
  year={1974},
  publisher={Cambridge University Press}
}

@article{schmitt2001,
  title={Stochastic equations generating continuous multiplicative cascades},
  author={Schmitt, F. G. and Marsan, D.},
  journal={Eur. Phys. J. B},
  volume={20},
  pages={3--6},
  year={2001},
  publisher={Springer}
}

@inproceedings{yaglom1966,
  title={The influence of fluctuations in energy dissipation on the shape of turbulence characteristics in the inertial interval},
  author={Yaglom, A. M.},
  booktitle={Sov. Phys. Dokl.},
  volume={11},
  pages={26},
  year={1966}
}

@article{yeungpope1989,
  title={Lagrangian statistics from direct numerical simulations of isotropic turbulence},
  author={Yeung, P. K. and Pope, S. B.},
  journal={J. Fluid Mech.},
  volume={207},
  pages={531--586},
  year={1989},
  publisher={Cambridge University Press}
}

@article{barralmandelbrot2002,
  title={Multifractal products of cylindrical pulses},
  author={Barral, J. and Mandelbrot, B. B.},
  journal={Probab. Theory Rel.},
  volume={124},
  number={3},
  pages={409--430},
  year={2002},
  publisher={Springer}
}

@article{schmittmarsan2001,
  title={Stochastic equations generating continuous multiplicative cascades},
  author={Schmitt, F. G. and Marsan, D.},
  journal={Eur. Phys. J. B},
  volume={20},
  pages={3--6},
  year={2001},
  publisher={Springer}
}

@article{arneodo1998prl,
  title={Analysis of random cascades using space-scale correlation functions},
  author={Arneodo, A. and Bacry, E. and Manneville, S. and Muzy, J.-F.},
  journal={Phys. Rev. Lett.},
  volume={80},
  pages={708},
  year={1998},
  publisher={APS}
}

@article{arneodo1998jmathphys,
  title={Random cascades on wavelet dyadic trees},
  author={Arneodo, A. and Bacry, E. and Muzy, J.-F.},
  journal={J. Math. Phys},
  volume={39},
  pages={4142--4164},
  year={1998},
  publisher={AIP}
}

@article{schertzer1987,
  title={Physical modeling and analysis of rain and clouds by anisotropic scaling multiplicative processes},
  author={Schertzer, D. and Lovejoy, S.},
  journal={J. Geophys. Res.-Atmos.},
  volume={92},
  pages={9693--9714},
  year={1987},
  publisher={Wiley Online Library}
}

@incollection{schertzer1991,
  author={Schertzer, D. and Lovejoy, S.},
  booktitle={Scaling, fractals and non-linear variability in geophysics},
  pages={41},
  year={1991},
  publisher={Kluwer, Berlin}
}

@article{bacry2001,
  title={Multifractal random walk},
  author={Bacry, E. and Delour, J. and Muzy, J.-F.},
  journal={Phys. Rev. E},
  volume={64},
  pages={026103},
  year={2001},
  publisher={APS}
}

@article{duplantier2014,
  title={Liouville quantum gravity as a mating of trees},
  author={Duplantier, B. and Miller, J. and Sheffield, S.},
  journal={arXiv preprint arXiv:1409.7055},
  year={2014}
}

@article{fyodorov2014,
  title={Freezing transitions and extreme values: random matrix theory, and disordered landscapes},
  author={Fyodorov, Y. V. and Keating, J. P.},
  journal={Philos. T. R. Soc. A},
  volume={372},
  pages={20120503},
  year={2014},
  publisher={The Royal Society Publishing.}
}

@article{duchon2012,
  title={Forecasting volatility with the multifractal random walk model},
  author={Duchon, J. and Robert, R. and Vargas, V.},
  journal={Math. Financ.},
  volume={22},
  pages={83--108},
  year={2012},
  publisher={Wiley Online Library}
}

@article{ripley1990,
  title={Finding spiral structures in images of galaxies},
  author={Ripley, B. D. and Sutherland, A. L.},
  journal={Philos. T. Roy. Soc. A},
  volume={332},
  pages={477--485},
  year={1990},
  publisher={The Royal Society London}
}

% particles / spheroids in turbulence
@article{zhao2015,
  title={Rotation of nonspherical particles in turbulent channel flow},
  author={Zhao, L. and Challabotla, N. R. and Andersson, H. I. and Variano, E.},
  journal={Phys. Rev. Lett.},
  volume={115},
  number={24},
  pages={244501},
  year={2015},
  publisher={APS}
}

@article{challabotla2015,
  title={Orientation and rotation of inertial disk particles in wall turbulence},
  author={Challabotla, N. R. and Zhao, L. and Andersson, H. I.},
  journal={J. Fluid Mech.},
  volume={766},
  year={2015},
  publisher={Cambridge University Press}
}

@article{byron2015,
  title={Shape-dependence of particle rotation in isotropic turbulence},
  author={Byron, M. and Einarsson, J. and Gustavsson, K. and Voth, G. and Mehlig, B. and Variano, E.},
  journal={Phys. Fluids},
  volume={27},
  pages={035101},
  year={2015},
  publisher={AIP Publishing LLC}
}

@article{gustavsson2014,
  title={Tumbling of small axisymmetric particles in random and turbulent flows},
  author={Gustavsson, K. and Einarsson, J. and Mehlig, B.},
  journal={Phys. Rev. Lett.},
  volume={112},
  pages={014501},
  year={2014},
  publisher={APS}
}

@article{parsa2012,
  title={Rotation rate of rods in turbulent fluid flow},
  author={Parsa, S. and Calzavarini, E. and Toschi, F. and Voth, G.},
  journal={Phys. Rev. Lett.},
  volume={109},
  number={13},
  pages={134501},
  year={2012},
  publisher={APS}
}

% experiments, structures and intermittency
@article{debue2018prf,
  title={{Experimental test of the crossover between the inertial and the dissipative range in a turbulent swirling flow}},
  author={Debue, P. and Kuzzay, D. and Saw, E.-W. and Daviaud, F. and Dubrulle, B. and Canet, L. and Rossetto, V. and Wschebor, N.},
  journal={Phys. Rev. Fluids},
  volume={3},
  pages={024602},
  year={2018},
  publisher={APS}
}

@article{debue2018pre,
  title={Dissipation, intermittency, and singularities in incompressible turbulent flows},
  author={Debue, P. and Shukla, V. and Kuzzay, D. and Faranda, D. and Saw, E.-W. and Daviaud, F. and Dubrulle, B.},
  journal={Phys. Rev. E},
  volume={97},
  pages={053101},
  year={2018},
  publisher={APS}
}

@article{barjona2017,
  title={{Kolmogorov's Lagrangian similarity law revisited}},
  author={Barjona, M. and da Silva, C. B.},
  journal={Phys. Fluids},
  volume={29},
  pages={105106},
  year={2017},
  publisher={AIP Publishing LLC}
}

@article{bacry2008,
  title={{Log-Normal continuous cascades: aggregation properties and estimation. Application to financial time-series}},
  author={Bacry, E. and Kozhemyak, A. and Muzy, J.-F.},
  journal={arXiv preprint arXiv:0804.0185},
  year={2008}
}

@article{muzy2000,
  title={Modelling fluctuations of financial time series: from cascade process to stochastic volatility model},
  author={Muzy, J.-F. and Delour, J. and Bacry, E.},
  journal={Eur. Phys. J. B},
  volume={17},
  number={3},
  pages={537--548},
  year={2000},
  publisher={Springer}
}

@book{bouchaud2003,
  title={Theory of financial risk and derivative pricing: from statistical physics to risk management},
  author={Bouchaud, J.-P. and Potters, M.},
  year={2003},
  publisher={Cambridge university press}
}

@article{mandelbrot1997,
  title={A multifractal model of asset returns},
  author={Mandelbrot, B. B. and Fisher, A. J. and Calvet, L. E.},
  year={1997},
  publisher={Cowles Foundation}
}

@article{ghashghaie1996,
  title={Turbulent cascades in foreign exchange markets},
  author={Ghashghaie, S. and Breymann, W. and Peinke, J. and Talkner, P. and Dodge, Y.},
  journal={Nature},
  volume={381},
  pages={767--770},
  year={1996},
  publisher={Nature Publishing Group}
}

@article{coles1991,
  title={A lognormal model for the cosmological mass distribution},
  author={Coles, P. and Jones, B.},
  journal={Mon. Not. R. Astron. Soc.},
  volume={248},
  pages={1--13},
  year={1991},
  publisher={The Royal Astronomical Society}
}

@article{frankot1987, 
  title={Lognormal random-field models and their applications to radar image synthesis},
  author={Frankot, R. T. and Chellappa, R.},
  journal={IEEE T. Geosci. Remote},
  pages={195--207},
  year={1987},
  publisher={IEEE}
}

@article{andersen2007,
  title={{Roughing it up: Including jump components in the measurement, modeling, and forecasting of return volatility}},
  author={Andersen, T. G. and Bollerslev, T. and Diebold, F. X.},
  journal={Rev. Econ. Statistics},
  volume={89},
  pages={701--720},
  year={2007},
  publisher={MIT Press}
}

@article{benzi2009,
  title={{Velocity-gradient statistics along particle trajectories in turbulent flows: The refined similarity hypothesis in the Lagrangian frame}},
  author={Benzi, R. and Biferale, L. and Calzavarini, E. and Lohse, D. and Toschi, F.},
  journal={Phys. Rev. E},
  volume={80},
  pages={066318},
  year={2009},
  publisher={APS}
}

@article{yeung2002,
  title={Lagrangian investigations of turbulence},
  author={Yeung, P. K.},
  journal={Annu. Rev. Fluid Mech.},
  volume={34},
  pages={115--142},
  year={2002},
  publisher={Annual Reviews}
}

@article{sawfordyeung2011,
  title={{Kolmogorov similarity scaling for one-particle Lagrangian statistics}},
  author={Sawford, B. L. and Yeung, P. K.},
  journal={Phys. Fluids},
  volume={23},
  pages={091704},
  year={2011},
  publisher={American Institute of Physics}
}

% small scale turbulence, long range correlations
@article{sreenivasanantonia1997,
  title={The phenomenology of small-scale turbulence},
  author={Sreenivasan, K. R. and Antonia, R. A.},
  journal={Annu. Rev. Fluid Mech.},
  volume={29},
  pages={435--472},
  year={1997},
  publisher={Annual Reviews}
}

@article{meneveausreenivasan1991,
  title={The multifractal nature of turbulent energy dissipation},
  author={Meneveau, C. and Sreenivasan, K. R.},
  journal={J. Fluid Mech.},
  volume={224},
  pages={429--484},
  year={1991},
  publisher={Cambridge University Press}
}

@article{gurvichyaglom1967,
  title={Breakdown of eddies and probability distributions for small-scale turbulence},
  author={Gurvich, A. S. and Yaglom, A. M.},
  journal={Phys. Fluids},
  volume={10},
  pages={S59--S65},
  year={1967},
  publisher={American Institute of Physics}
}

@article{motoori2019,
  title={Generation mechanism of a hierarchy of vortices in a turbulent boundary layer},
  author={Motoori, Y. and Goto, S.},
  journal={J. Fluid Mech.},
  volume={865},
  pages={1085--1109},
  year={2019},
  publisher={Cambridge University Press}
}

@article{doan2018,
  title={Scale locality of the energy cascade using real space quantities},
  author={Doan, N. A. K. and Swaminathan, N. and Davidson, P. A. and Tanahashi, M.},
  journal={Phys. Rev. Fluids},
  volume={3},
  pages={084601},
  year={2018},
  publisher={APS}
}

@article{lejan1997,
  title={Stochastic cascades and 3-dimensional Navier--Stokes equations},
  author={Le Jan, Y. and Sznitman, A. S.},
  journal={Probab. Theory Rel.},
  volume={109},
  pages={343--366},
  year={1997},
  publisher={Springer}
}

% volatility is lognormal and long range correlated
@article{liu1999,
  title={Statistical properties of the volatility of price fluctuations},
  author={Liu, Y. and Gopikrishnan, P. and Stanley, H. E.},
  journal={Phys. Rev. E},
  volume={60},
  pages={1390},
  year={1999},
  publisher={APS}
}

% cond mat multifractal
@article{kravtsov1997,
  title={New class of random matrix ensembles with multifractal eigenvectors},
  author={Kravtsov, V. E. and Muttalib, K. A.},
  journal={Phys. Rev. Lett.},
  volume={79},
  pages={1913},
  year={1997},
  publisher={APS}
}

@article{serbyn2017,
  title={Thouless energy and multifractality across the many-body localization transition},
  author={Serbyn, M. and Papi{\'c}, Z. and Abanin, D. A.},
  journal={Phys. Rev. B},
  volume={96},
  pages={104201},
  year={2017},
  publisher={APS}
}

@article{schmitt1994,
  author = {Schmitt, F. G. and Schertzer, D. and Lovejoy, S. and Brunet, Y.},
  title = {Empirical study of multifractal phase transitions in atmospheric turbulence},
  journal = {Nonlinear Proc. Geoph.},
  volume = {1},
  year = {1994},
  pages = {95--104},
}

@article{lashermes2004,
  title={New insights into the estimation of scaling exponents},
  author={Lashermes, B. and Abry, P. and Chainais, P.},
  journal={Int. J. Wavelets Multi.},
  volume={2},
  pages={497--523},
  year={2004},
  publisher={World Scientific}
}

% Euler intermittency parameter measures
@article{stolovitzky1992,
  title={Kolmogorov's refined similarity hypotheses},
  author={Stolovitzky, G. and Kailasnath, P. and Sreenivasan, K. R.},
  journal={Phys. Rev. Lett.},
  volume={69},
  pages={1178},
  year={1992},
  publisher={APS}
}


@article{stolovitzky1994,
  title={Kolmogorov's refined similarity hypotheses for turbulence and general stochastic processes},
  author={Stolovitzky, G. and Sreenivasan, K. R.},
  journal={Rev. Mod. Phys.},
  volume={66},
  pages={229},
  year={1994},
  publisher={APS}
}

@article{praskovsky1997,
  title={Further experimental support for the Kolmogorov refined similarity hypothesis},
  author={Praskovsky, A. and Praskovskaya, E. and Horst, T.},
  journal={Phys. Fluids},
  volume={9},
  pages={2465--2467},
  year={1997},
  publisher={American Institute of Physics}
}

@article{chen1997,
  title={Refined similarity hypothesis for transverse structure functions in fluid turbulence},
  author={Chen, S. and Sreenivasan, K. R. and Nelkin, M. and Cao, N.},
  journal={Phys. Rev. Lett.},
  volume={79},
  number={12},
  pages={2253},
  year={1997},
  publisher={APS}
}

@article{borgas1993,
  title={{The multifractal Lagrangian nature of turbulence}},
  author={Borgas, M. S.},
  journal={Philos. T. Roy. Soc. A},
  volume={342},
  pages={379--411},
  year={1993},
  publisher={The Royal Society London}
}

@article{pereira2016,
  title={A dissipative random velocity field for fully developed fluid turbulence},
  author={Pereira, R. M. and Garban, C. and Chevillard, L.},
  journal={J. Fluid Mech.},
  volume={794},
  pages={369--408},
  year={2016},
  publisher={Cambridge University Press}
}

@article{morgado2016,
  title={{Thermostatistics of small nonlinear systems: Poissonian athermal bath}},
  author={Morgado, W. A. M. and Queir{\'o}s, S. M. D.},
  journal={Phys. Rev. E},
  volume={93},
  pages={012121},
  year={2016},
  publisher={APS}
}

@article{mandelbrot1974paris,
  title={Multiplications al{\'e}atoires it{\'e}r{\'e}es et distributions invariantes par moyenne pond{\'e}r{\'e}e al{\'e}atoire},
  author={Mandelbrot, B. B.},
  journal={C. R. Acad. Sci. Paris},
  volume={278},
  pages={355--358},
  year={1974}
}

@article{wiener1938,
  title={The homogeneous chaos},
  author={Wiener, N.},
  journal={Am. J. Math.},
  volume={60},
  pages={897--936},
  year={1938},
  publisher={JSTOR}
}

@article{blatman2011,
  title={Adaptive sparse polynomial chaos expansion based on least angle regression},
  author={Blatman, G. and Sudret, B.},
  journal={J. Comp. Phys.},
  volume={230},
  pages={2345--2367},
  year={2011},
  publisher={Elsevier}
}

@book{temam2001,
  title={Navier-Stokes equations: theory and numerical analysis},
  author={Temam, R.},
  volume={343},
  year={2001},
  publisher={American Mathematical Soc.}
}

@article{shen2007,
  title={A kinetic-theory based first order slip boundary condition for gas flow},
  author={Shen, S. and Chen, G. and Crone, R. M. and Anaya-Dufresne, M.},
  journal={Phys. Fluids},
  volume={19},
  pages={086101},
  year={2007},
  publisher={American Institute of Physics}
}

@article{denniston2006,
  title={General continuum boundary conditions for miscible binary fluids from molecular dynamics simulations},
  author={Denniston, C. and Robbins, M. O.},
  journal={J. Chem. Phys.},
  volume={125},
  pages={214102},
  year={2006},
  publisher={American Institute of Physics}
}

@article{arenas2010,
  title={Functional integral approach for multiplicative stochastic processes},
  author={Arenas, Z. G. and Barci, D. G.},
  journal={Phys. Rev. E},
  volume={81},
  pages={051113},
  year={2010},
  publisher={APS}
}

@article{janssen1992,
  title={From Phase Transitions to Chaos},
  author={Janssen, H. K.},
  journal={Topics in Modern Statistical Physics},
  year={1992},
  publisher={World Scientific Singapore}
}
