\documentclass[12pt,a4paper,twoside,BCOR=1cm]{scrreprt}

\usepackage{amsmath, amsthm, amssymb}
\usepackage{mathtools}
\usepackage{grffile}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{subfig}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{newapave}
\usepackage{xcolor}
\usepackage{hyperref} 
\usepackage{setspace}
\usepackage{units}
\usepackage[stable,perpage,symbol*,multiple]{footmisc}
\usepackage[tracking=true,kerning=true,spacing=true,babel]{microtype}
\usepackage[utf8]{inputenc}
\usepackage[final]{pdfpages}

%\synctex=1



\hypersetup{
 colorlinks=true,
 citecolor=teal,
 linkcolor=blue,
 urlcolor=cyan,
 hyperfigures=true}

\graphicspath{%
{figs/illustrations/}%
{figs/input/}%
{figs/results/}%
{figs/presentation/}%
} 


\newtheorem{thm}{Theorem}[chapter]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{defn}{Definition}[chapter]


% Add some helper macros.
\DeclareMathOperator*{\vect}{\mathrm{vec}}
\renewcommand\Re{\operatorname{Re}}
\renewcommand\Im{\operatorname{Im}}


%\title{Numerical methods for phase retrieval}
%\author{Eliyahu Osherovich}
%\date{\today{}}


\begin{document}


% \maketitle
\include{front/cover}
\pagenumbering{roman}
\include{front/front}
\include{front/acknowledgments}

\tableofcontents
\listoffigures
%\listoftables



\begin{abstract}
  In this work we consider the problem of reconstruction of a signal
  from the magnitude of its Fourier transform, also known as phase
  retrieval. The problem arises in many areas of astronomy,
  crystallography, optics, and coherent diffraction imaging (CDI). Our
  main goal is to develop an efficient reconstruction method based on
  continuous optimization techniques. Unlike current reconstruction
  methods, which are based on alternating projections, our approach
  leads to a much faster and more robust method. However, all previous
  attempts to employ continuous optimization methods, such as
  Newton-type algorithms, to the phase retrieval problem failed. In this
  work we provide an explanation for this failure, and based on this
  explanation we devise a sufficient condition that allows development
  of new reconstruction methods---approximately known Fourier phase. We
  demonstrate that a rough (up to $\pi/2$ radians) Fourier phase
  estimate practically guarantees successful reconstruction by any
  reasonable method. We also present a new reconstruction method whose
  reconstruction time is orders of magnitude faster than that of the
  current method-of-choice in phase retrieval---Hybrid Input-Output
  (HIO). Moreover, our method is capable of successful reconstruction
  even in the situations where HIO is known to fail. We also extended
  our method to other applications: Fourier domain holography, and
  interferometry.

  Additionally we\footnote{The work on sub-wavelength CDI was done in
    collaboration with Prof. M.~Segev's group from the Technion
    Physics Department, Solid State Institute.} developed a new
  sparsity-based method for sub-wavelength CDI. Using this method we
  demonstrated experimental resolution exceeding several times the
  physical limit imposed by the diffraction light properties (so
  called diffraction limit).
\end{abstract}

\cleardoublepage{}
\pagenumbering{arabic}

%\begin{doublespacing}

\include{intro/intro}

%\include{physics/physics}

\include{mathematics/mathematics}

\include{current_methods/current_methods}

\include{optimization/optimization}

\include{phase-empirical/phase-empirical}

\include{phase-theory/phase-theory}

\include{phase-holography/phase-holography}

\include{boundary/boundary}

\include{sparsity/sparsity}

\include{afterword/afterword}

\bibliographystyle{newapave}
\bibliography{My_Library}

%\end{doublespacing}
%\includepdf[pages=-]{hebrew_reversed.pdf}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:
